---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-19"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Durchschnittsalter Mütter erstgebärend

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-durchschnittsalter-muetter-erstgebaerend)

Auto generated R starter code for data set 100@lhm.

## Metadata

- **Issued** `2016-11-14T08:05:21`
- **Modified** `2023-07-27T06:57:02`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Frauen', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-durchschnittsalter-muetter-erstgebaerend`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1001
# Title                    : Durchschnittsalter Mütter erstgebärend
# Issued                   : 2016-11-14T09:59:15
# Modified                 : 2023-07-27T06:57:02
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/86ddee28-69b2-4e8a-85d2-1651bd50833a/resource/2203038a-7a12-4f6d-b8c7-7df37397d4f2/download/indikat_bevoelkerung_durchschnittsalter_muetter_erstgebaerend_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
