---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-10"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Durchschnittsalter

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-durchschnittsalter-83r65mct)

Auto generated R starter code for data set 102@lhm.

## Metadata

- **Issued** `2015-01-26T13:02:18`
- **Modified** `2023-07-27T06:46:58`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-durchschnittsalter-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1021
# Title                    : Altersdurchschnitt
# Issued                   : 2015-01-26T14:02:19
# Modified                 : 2023-07-27T06:46:58
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/9b072087-6098-4558-b221-01e7d119b512/resource/9177f886-7341-49d2-9bfa-15d4d8631327/download/indikat_bevoelkerung_durchschnittsalter_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
