---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-22"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Außenwanderungsziffer Kinder bis 13 Jahre

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/105@lhm)

Auto generated R starter code for data set 105@lhm.

## Metadata

- **Issued** `2015-01-26T13:05:27`
- **Modified** `2023-07-27T06:23:25`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Indikatorenatlas', 'Kinder', 'Wanderungen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-aussenwanderungsziffer-kinder-bis-13-jahre-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1051
# Title                    : Außenwanderungsziffer Kinder unter 14 Jahre
# Description              : abcdefg
# Issued                   : 2015-01-26T14:05:28
# Modified                 : 2023-01-04T09:02:49
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/ee2e0ef7-c256-42d6-a5e7-949cbb4e1905/resource/604650ad-240a-4a94-9649-664c5d1e1c19/download/indikatorenatlas2209_bevoelkerung_aussenwanderungsziffer_kinder_unter_14_jahre.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
