---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-21"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Altenquotient

abcdefg

[Direct data shop link for dataset](XYZ110@lhm)

Auto generated R starter code for data set 110@lhm.

## Metadata

- **Issued** `2015-01-26T13:02:10`
- **Modified** `2023-07-27T05:58:41`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Alter', 'Bevölkerung', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-altenquotient-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1101
# Title                    : Altenquotient
# Description              : abcdefg
# Issued                   : 2015-01-26T14:02:11
# Modified                 : 2023-07-27T05:54:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4d161816-0583-4713-8048-9ada492ecfae/resource/0a471ad2-0e4e-4a6b-815d-b461253a9ee2/download/indikat_bevoelkerung_altenquotient_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
