---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-16"
output: html_document
---

## Dataset: Oktoberfest

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/oktoberfest)

Auto generated R starter code for data set 115@lhm.

## Metadata

- **Issued** `2014-12-16T14:15:40`
- **Modified** `2023-07-24T06:14:26`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bier', 'Bierpreis', 'Hendl', 'Oktoberfest', 'Wiesn']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/oktoberfest`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1151
# Title                    : Oktoberfest 1985 - 2022
# Issued                   : 2014-12-16T15:16:11
# Modified                 : 2023-07-24T06:04:48
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/e0f664cf-6dd9-4743-bd2b-81a8b18bd1d2/download/oktoberfestgesamt19852022.csv')

# Distribution 1
# Ktzhdistid               : 1152
# Title                    : Oktoberfest Bierkonsum 1985 - 2022
# Issued                   : 2014-12-16T15:21:21
# Modified                 : 2023-07-24T06:05:50
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/56a0c3c8-c2ea-4b42-bbd2-21cb72d80803/download/oktoberfestbierkonsum19852022.csv')

# Distribution 2
# Ktzhdistid               : 1153
# Title                    : Oktoberfest Bierpreise 1985 - 2022
# Issued                   : 2014-12-16T15:25:07
# Modified                 : 2023-07-24T06:06:19
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/52fda541-c4dd-4eb6-8f2a-84ca24ffe775/download/oktoberfestbierpreis19852022.csv')

# Distribution 3
# Ktzhdistid               : 1154
# Title                    : Oktoberfest Besucherinnen und Besucher 1985 - 2022
# Issued                   : 2014-12-16T15:34:47
# Modified                 : 2023-07-24T06:06:42
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8d6c8251-7956-4f92-8c96-f79106aab828/resource/902cafb5-0523-4114-a46c-7cd8240b1347/download/oktoberfestbesucher19852022.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
