---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-28"
output: html_document
---

## Dataset: Monatszahlen Verkehrsunfälle

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-verkehrsunfaelle)

Auto generated R starter code for data set 117@lhm.

## Metadata

- **Issued** `2017-02-20T15:03:38`
- **Modified** `2023-07-20T06:05:33`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-verkehrsunfaelle`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1171
# Title                    : Monatszahlen Verkehrsunfälle
# Issued                   : 2017-02-20T16:03:59
# Modified                 : 2023-07-20T06:05:23
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/5e73a82b-7cfb-40cc-9b30-45fe5a3fa24e/resource/40094bd6-f82d-4979-949b-26c8dc00b9a7/download/monatszahlen2307_verkehrsunfaelle_10_07_23_nosum.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.dir@muenchen.de
