---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-09"
output: html_document
---

## Dataset: Monatszahlen Witterung

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-witterung)

Auto generated R starter code for data set 120@lhm.

## Metadata

- **Issued** `2017-02-21T14:59:41`
- **Modified** `2023-07-20T06:01:30`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-witterung`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1201
# Title                    : Monatszahlen Witterung
# Issued                   : 2017-02-21T15:59:53
# Modified                 : 2023-07-20T06:01:19
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/d7e42935-8884-40d3-9284-096d9cafecdd/resource/64c8c183-7fd0-4b29-9958-4169d22ee883/download/monatszahlen2307_witterung_10_07_23_nosum.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.dir@muenchen.de
