---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-31"
output: html_document
---

## Dataset: Monatszahlen Einbürgerungen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-einbuergerungen)

Auto generated R starter code for data set 130@lhm.

## Metadata

- **Issued** `2017-02-20T10:20:10`
- **Modified** `2023-07-20T05:52:33`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-einbuergerungen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1301
# Title                    : Monatszahlen Einbürgerungen
# Issued                   : 2017-02-20T11:20:25
# Modified                 : 2023-07-20T05:51:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/5420c698-0bc4-4711-b1db-0c0b40f5cd2f/resource/412fe83d-30c0-41c3-8b5b-482fb890406f/download/monatszahlen2307_einbuergerungen_10_07_23_nosum.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.amt@muenchen.de
