---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-02"
output: html_document
---

## Dataset: Monatszahlen Arbeitsmarkt

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-arbeitsmarkt)

Auto generated R starter code for data set 132@lhm.

## Metadata

- **Issued** `2017-02-20T10:26:08`
- **Modified** `2023-07-20T05:50:11`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-arbeitsmarkt`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1321
# Title                    : Monatszahlen Arbeitsmarkt
# Issued                   : 2017-02-20T11:26:19
# Modified                 : 2023-07-20T05:45:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/5508548a-db7e-49f1-a77e-b0763b00eb97/resource/0b6fe83d-4bf9-4789-9752-a3aefb073020/download/monatszahlen2307_arbeitsmarkt_10_07_23_nosum.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.dir@muenchen.de
