---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-20"
output: html_document
---

## Dataset: Monatszahlen Bauen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-bauen)

Auto generated R starter code for data set 133@lhm.

## Metadata

- **Issued** `2017-02-20T13:08:03`
- **Modified** `2023-07-20T05:49:43`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-bauen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1331
# Title                    : Monatszahlen Bauen
# Issued                   : 2017-02-20T14:08:15
# Modified                 : 2023-07-20T05:47:16
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/6c05f063-8113-4fee-9b52-57fca7211b36/resource/bba34051-1a32-43c7-bb46-09270e708570/download/monatszahlen2307_bauen_10_07_23_nosum.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.dir@muenchen.de
