---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-23"
output: html_document
---

## Dataset: Kindertagesbetreuungseinrichtungen in München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/kindertagesbetreuungseinrichtungen-in-muenchen)

Auto generated R starter code for data set 134@lhm.

## Metadata

- **Issued** `2023-06-23T06:26:15`
- **Modified** `2023-06-23T06:51:32`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Kinder', 'Kindertageseinrichtungen', 'Kindertagesstätten', 'Kitas', 'Stadtratsauftrag']`
- **Publisher** `['referat-fur-bildung-und-sport']`
- **Landingpage** `https://opendata.muenchen.de/dataset/kindertagesbetreuungseinrichtungen-in-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1341
# Title                    : Kita-Einrichtungen
# Issued                   : 2023-06-23T06:28:00
# Modified                 : 2023-06-23T06:28:00
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/21d97a9e-1e94-4a0c-86d1-3c1539bcb18b/resource/b6e9a48f-4892-47c4-ae97-37d1bc7ec993/download/open_data_kitas_2023_04_18.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

RBS-KITA-SuG-Datenmanagement | Data Shop | 
