---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-12-05"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München - Jahreszahlen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-jahreszahlen)

Auto generated R starter code for data set 135@lhm.

## Metadata

- **Issued** `2023-01-26T14:19:20`
- **Modified** `2023-06-22T09:39:00`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Rad', 'Raddauerzählstellen']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-jahreszahlen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 30 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1351
# Title                    : 15 Minuten Werte 2008
# Issued                   : 2023-02-16T10:36:03
# Modified                 : 2023-06-22T06:09:55
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/66be7619-a672-4382-bf88-e3688c5abc2b/download/rad_2008_15min_06_06_23_r.csv')

# Distribution 1
# Ktzhdistid               : 1352
# Title                    : Tageswerte Wetter 2008
# Issued                   : 2023-02-16T10:34:48
# Modified                 : 2023-06-21T14:24:01
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/53ef8c4b-d411-477f-9cf3-b044a4c1aaaa/download/rad_2008_tage_19_06_23_r.csv')

# Distribution 2
# Ktzhdistid               : 1353
# Title                    : 15 Minuten Werte 2009
# Issued                   : 2023-02-16T10:37:37
# Modified                 : 2023-06-22T06:18:31
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/3ef8aad9-a6b0-4c97-a6b7-8c3a63226b37/download/rad_2009_15min_06_06_23_r.csv')

# Distribution 3
# Ktzhdistid               : 1354
# Title                    : Tageswerte Wetter 2009
# Issued                   : 2023-02-16T10:34:26
# Modified                 : 2023-06-21T14:45:35
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/89dbef6c-c6cb-4bfc-8729-93049e91223d/download/rad_2009_tage_19_06_23_r.csv')

# Distribution 4
# Ktzhdistid               : 1355
# Title                    : 15 Minuten Werte 2010
# Issued                   : 2023-02-16T10:39:22
# Modified                 : 2023-06-22T06:23:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/6558a5f9-2c96-4e4b-985d-8eb99b7b73b1/download/rad_2010_15min_06_06_23_r.csv')

# Distribution 5
# Ktzhdistid               : 1356
# Title                    : Tageswerte Wetter 2010
# Issued                   : 2023-02-16T10:34:02
# Modified                 : 2023-06-21T14:46:34
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/cb720004-bcde-4c0e-babf-64ee995c5232/download/rad_2010_tage_19_06_23_r.csv')

# Distribution 6
# Ktzhdistid               : 1357
# Title                    : 15 Minuten Werte 2011
# Issued                   : 2023-02-16T10:43:11
# Modified                 : 2023-06-22T06:28:05
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/86962013-4854-4deb-aaf9-36e3770cde24/download/rad_2012_15min_06_06_23_r.csv')

# Distribution 7
# Ktzhdistid               : 1358
# Title                    : Tageswerte Wetter 2011
# Issued                   : 2023-02-16T10:33:32
# Modified                 : 2023-06-21T14:46:58
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/8c752f92-2cb3-4765-aecf-bda349592ab2/download/rad_2011_tage_19_06_23_r.csv')

# Distribution 8
# Ktzhdistid               : 1359
# Title                    : 15 Minuten Werte 2012
# Issued                   : 2023-02-16T10:45:39
# Modified                 : 2023-06-22T06:31:20
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/ff5d2ebf-dde6-4f21-9c68-2aab74addeec/download/rad_2012_15min_06_06_23_r.csv')

# Distribution 9
# Ktzhdistid               : 1360
# Title                    : Tageswerte Wetter 2012
# Issued                   : 2023-02-16T10:32:54
# Modified                 : 2023-06-21T14:47:20
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/7304e087-e02d-4ca1-b4da-5c46b27fa223/download/rad_2012_tage_19_06_23_r.csv')

# Distribution 10
# Ktzhdistid               : 1361
# Title                    : 15 Minuten Werte 2013
# Issued                   : 2023-02-10T15:55:12
# Modified                 : 2023-06-22T06:34:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/9f4f798f-0ad1-4e86-8157-15c5e46eaf91/download/rad_2013_15min_06_06_23_r.csv')

# Distribution 11
# Ktzhdistid               : 1362
# Title                    : Tageswerte Wetter 2013
# Issued                   : 2023-02-10T16:03:27
# Modified                 : 2023-06-21T14:47:45
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/e281aac1-c476-48da-84ce-2bf52bf20a08/download/rad_2013_tage_19_06_23_r.csv')

# Distribution 12
# Ktzhdistid               : 1363
# Title                    : 15 Minuten Werte 2014
# Issued                   : 2023-02-10T15:50:02
# Modified                 : 2023-06-22T06:37:17
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/784b925b-1d5f-43d3-8353-fd5d02fc7c53/download/rad_2014_15min_06_06_23_r.csv')

# Distribution 13
# Ktzhdistid               : 1364
# Title                    : Tageswerte Wetter 2014
# Issued                   : 2023-02-10T15:47:45
# Modified                 : 2023-06-21T14:48:37
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/b78e7a05-33a5-422c-98fa-27c5cf9afe81/download/rad_2014_tage_19_06_23_r.csv')

# Distribution 14
# Ktzhdistid               : 1365
# Title                    : 15 Minuten Werte 2015
# Issued                   : 2023-02-10T15:33:56
# Modified                 : 2023-06-22T06:39:56
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/d6b3a72c-b180-40a0-a2ab-d97040737f20/download/rad_2015_15min_06_06_23_r.csv')

# Distribution 15
# Ktzhdistid               : 1366
# Title                    : Tageswerte Wetter 2015
# Issued                   : 2023-02-10T15:38:34
# Modified                 : 2023-06-21T14:49:07
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/d5dd6fda-77ee-4ac7-9c7f-af54ccea64e4/download/rad_2015_tage_19_06_23_r.csv')

# Distribution 16
# Ktzhdistid               : 1367
# Title                    : 15 Minuten Werte 2016
# Issued                   : 2023-02-10T14:42:09
# Modified                 : 2023-06-22T06:46:05
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/3913d9e6-1be8-4ee4-ab88-1266cbf161f1/download/rad_2016_15min_06_06_23_r.csv')

# Distribution 17
# Ktzhdistid               : 1368
# Title                    : Tageswerte Wetter 2016
# Issued                   : 2023-02-10T14:57:53
# Modified                 : 2023-06-21T14:49:31
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/2f9e99cf-e82d-41fb-990c-67783cf23ab7/download/rad_2016_tage_19_06_23_r.csv')

# Distribution 18
# Ktzhdistid               : 1369
# Title                    : 15 Minuten Werte 2017
# Issued                   : 2023-01-26T14:24:16
# Modified                 : 2023-06-22T06:51:28
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/694b9927-b4d5-4e8f-9c62-09b8ac03c39a/download/rad_2017_15min_06_06_23_r.csv')

# Distribution 19
# Ktzhdistid               : 1370
# Title                    : Tageswerte Wetter 2017
# Issued                   : 2023-01-26T14:26:12
# Modified                 : 2023-06-21T14:49:53
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/d584bb5e-021b-43ea-8d32-8ba6c92b8f1e/download/rad_2017_tage_19_06_23_r.csv')

# Distribution 20
# Ktzhdistid               : 1371
# Title                    : 15 Minuten Werte 2018
# Issued                   : 2023-01-26T14:30:50
# Modified                 : 2023-06-22T07:32:48
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/0a97a624-daa4-4cd8-a820-7d2fa6ffe89a/download/rad_2018_15min_06_06_23_r.csv')

# Distribution 21
# Ktzhdistid               : 1372
# Title                    : Tageswerte Wetter 2018
# Issued                   : 2023-01-26T14:31:46
# Modified                 : 2023-06-21T14:50:18
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/00c5eaf9-d464-433f-8c9b-ce8a2a16db2b/download/rad_2018_tage_19_06_23_r.csv')

# Distribution 22
# Ktzhdistid               : 1373
# Title                    : 15 Minuten Werte 2019
# Issued                   : 2023-01-26T14:35:41
# Modified                 : 2023-06-22T07:14:27
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/893e1f16-6504-4f4f-b8b3-f907ef406cd5/download/rad_2019_15min_06_06_23_r.csv')

# Distribution 23
# Ktzhdistid               : 1374
# Title                    : Tageswerte Wetter 2019
# Issued                   : 2023-01-26T14:38:34
# Modified                 : 2023-06-21T14:50:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/f6d559cc-9e30-4307-b005-7b105b967ec0/download/rad_2019_tage_19_06_23_r.csv')

# Distribution 24
# Ktzhdistid               : 1375
# Title                    : 15 Minuten Werte 2020
# Issued                   : 2023-01-26T14:42:33
# Modified                 : 2023-06-22T07:19:03
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/9be77b23-a444-4ba5-be9e-7f8594aa0188/download/rad_2020_15min_06_06_23_r.csv')

# Distribution 25
# Ktzhdistid               : 1376
# Title                    : Tageswerte Wetter 2020
# Issued                   : 2023-01-26T14:48:02
# Modified                 : 2023-06-21T14:51:05
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/8ae44963-171e-4edf-bf16-f12503717042/download/rad_2020_tage_19_06_23_r.csv')

# Distribution 26
# Ktzhdistid               : 1377
# Title                    : 15 Minuten Werte 2021
# Issued                   : 2023-01-26T14:56:27
# Modified                 : 2023-06-22T06:57:21
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/205c5c9e-9689-4c28-97cb-e575c6c772ce/download/rad_2021_15min_06_06_23_r.csv')

# Distribution 27
# Ktzhdistid               : 1378
# Title                    : Tageswerte Wetter 2021
# Issued                   : 2023-01-26T14:57:21
# Modified                 : 2023-06-21T14:51:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/561fb0d5-2d27-41bb-bda9-a383d6d42ad1/download/rad_2021_tage_19_06_23_r.csv')

# Distribution 28
# Ktzhdistid               : 1379
# Title                    : 15 Minuten Werte 2022
# Issued                   : 2023-01-26T15:01:40
# Modified                 : 2023-06-22T06:54:32
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/e65e0e26-ce1f-4e58-9260-beccac196e75/download/rad_2022_15min_06_06_23_r.csv')

# Distribution 29
# Ktzhdistid               : 1380
# Title                    : Tageswerte Wetter 2022
# Issued                   : 2023-01-26T15:03:12
# Modified                 : 2023-06-21T14:51:50
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/022a11ff-4dcb-4f03-b7dd-a6c94a094587/resource/05a2178d-3138-4874-a9fd-1ede6f0cedc1/download/rad_2022_tage_19_06_23_r.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
