---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-23"
output: html_document
---

## Dataset: B + R Anlagen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/b-r-anlagen)

Auto generated R starter code for data set 137@lhm.

## Metadata

- **Issued** `2022-11-15T07:22:12`
- **Modified** `2023-04-12T12:51:46`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Stadtratsauftrag']`
- **Publisher** `['p-r-park-ride-gmbh-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/b-r-anlagen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1371
# Title                    : B+R Anlagen Übersicht
# Issued                   : 2022-11-15T07:23:13
# Modified                 : 2023-04-12T12:51:46
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/3746194a-164b-46c4-8fc7-367a83833a9d/resource/aba62755-1a22-4fa8-a371-3629b6b39e39/download/br-anlagen-uebersicht-stand-03-2023-mit-koordinaten.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
