---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-27"
output: html_document
---

## Dataset: Munich IT Dashboard

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/munich-it-dashboard)

Auto generated R starter code for data set 138@lhm.

## Metadata

- **Issued** `2023-03-09T07:05:44`
- **Modified** `2023-03-10T09:06:04`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `[]`
- **Publisher** `['it-referat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/munich-it-dashboard`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1381
# Title                    : Software bei der LHM
# Issued                   : 2023-03-09T07:07:26
# Modified                 : 2023-03-09T07:07:26
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/faedfa85-a3f9-45dc-ac62-d90f2b5923c5/resource/5bf4ea36-f65c-4808-bc3a-4a7a8d48dc92/download/2023-03_veroeffentlichung-als-opendata-4.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

beschluesse.rit@muuenchen.de | Data Shop | 
