---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-28"
output: html_document
---

## Dataset: Hallensportprogramm

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/hallensportprogramm)

Auto generated R starter code for data set 139@lhm.

## Metadata

- **Issued** `2023-03-07T06:33:58`
- **Modified** `2023-03-10T07:32:14`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Sport', 'Stadtratsauftrag']`
- **Publisher** `['referat-fur-bildung-und-sport']`
- **Landingpage** `https://opendata.muenchen.de/dataset/hallensportprogramm`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1391
# Title                    : Hallensportprogramm
# Issued                   : 2023-03-07T06:35:55
# Modified                 : 2023-03-07T06:35:55
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2e8a06d3-3b9d-4a4f-a19d-bc9bb74db160/resource/c242c94b-4d18-4259-90a5-7e474179de47/download/opendata_hallenprogramm_2022_2023.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

freizeitsport@muenchen.de | Data Shop | 
