---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-17"
output: html_document
---

## Dataset: Staatsquote des Kantons Zürich

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/1401@finanzverwaltung-kanton-zuerich)

Auto generated R starter code for data set 1401@finanzverwaltung-kanton-zuerich.

## Metadata

- **Issued** `2022-06-07T11:05:44`
- **Modified** `2023-01-26T14:12:38`
- **Startdate** `2008-12-31`
- **Enddate** `2020-12-31`
- **Theme** `['Öffentliche Verwaltung und Finanzen']`
- **Keyword** `['finanzkennzahlen', 'oeffentliche_finanzen', 'staatsfinanzen', 'ogd']`
- **Publisher** `['Finanzverwaltung des Kantons Zürich']`
- **Landingpage** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2738
# Title                    : Staatsquote des Kantons Zürich ab 2008
# Description              : Variabeln: 'gesamtausgaben' und 'bruttoinlandprodukt' in Tausend CHF.
# Issued                   : 2022-06-07T11:05:44
# Modified                 : 2023-01-26T14:12:03
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00001401_00002738.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Finanzverwaltung des Kantons Zürich | Steuerung Finanzhaushalt | finanzhaushalt@fdfv.zh.ch
