---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-16"
output: html_document
---

## Dataset: Öffentliche Spielplätze München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/oeffentliche-spielplaetze-muenchen)

Auto generated R starter code for data set 141@lhm.

## Metadata

- **Issued** `2016-06-14T08:47:57`
- **Modified** `2023-02-15T10:04:51`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Isar', 'Spielen', 'Stadtratsauftrag']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/oeffentliche-spielplaetze-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1411
# Title                    : Öffentliche Spielplätze in München
# Issued                   : 2016-06-14T10:49:47
# Modified                 : 2023-02-15T09:57:28
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/0760ce3a-fef8-43e4-888f-8cc92fdf56de/resource/845ce3bd-ea80-4623-b51d-a30680175c22/download/spielplaetze_2b_2.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

eoGovernment Projekt Landeshauptstadt München | Data Shop | j-spartenanfrage.bau@muenchen.de
