---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-10"
output: html_document
---

## Dataset: Vornamen von Neugeborenen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen)

Auto generated R starter code for data set 143@lhm.

## Metadata

- **Issued** `2022-08-04T11:00:00`
- **Modified** `2023-01-27T08:26:48`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['München', 'Vornamen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 10 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1431
# Title                    : Vornamen 2013
# Issued                   : 2023-01-25T09:15:48
# Modified                 : 2023-01-25T09:15:48
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/17c4915d-6b8b-470f-a6b6-31f61b10a285/download/vornamen_2013.csv')

# Distribution 1
# Ktzhdistid               : 1432
# Title                    : Vornamen 2014
# Issued                   : 2023-01-25T09:16:41
# Modified                 : 2023-01-25T09:16:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/5d581ba3-4c7e-4057-8be1-04d56bb0d8d6/download/vornamen_2014.csv')

# Distribution 2
# Ktzhdistid               : 1433
# Title                    : Vornamen 2015
# Issued                   : 2023-01-25T09:19:24
# Modified                 : 2023-01-25T09:19:24
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/c11e8fef-94c8-4e16-a769-70dc6b98b69b/download/vornamen_2015.csv')

# Distribution 3
# Ktzhdistid               : 1434
# Title                    : Vornamen 2016
# Issued                   : 2023-01-25T09:21:20
# Modified                 : 2023-01-25T09:21:20
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/6655ec3c-251a-4a5e-9a57-d60c4ad59ca3/download/vornamen2016.csv')

# Distribution 4
# Ktzhdistid               : 1435
# Title                    : Vornamen 2017
# Issued                   : 2023-01-25T09:21:49
# Modified                 : 2023-01-25T09:21:49
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/2c70d289-8b1a-4071-9739-866c5e532b77/download/vornamen2017.csv')

# Distribution 5
# Ktzhdistid               : 1436
# Title                    : Vornamen 2018
# Issued                   : 2023-01-25T09:22:23
# Modified                 : 2023-01-25T09:22:23
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/23fdd53e-485a-46bd-abb6-d7a51b2ebb18/download/vornamen_2018.csv')

# Distribution 6
# Ktzhdistid               : 1437
# Title                    : Vornamen 2019
# Issued                   : 2023-01-25T09:23:25
# Modified                 : 2023-01-25T09:23:25
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/523d5860-25eb-4bea-96e3-193d1dacfb8f/download/vornamen2019.csv')

# Distribution 7
# Ktzhdistid               : 1438
# Title                    : Vornamen 2020
# Issued                   : 2023-01-25T09:24:00
# Modified                 : 2023-01-25T09:24:00
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/48a4c5fd-f5f2-4c0c-bcb3-222fd9ebda67/download/vornamen_2020.csv')

# Distribution 8
# Ktzhdistid               : 1439
# Title                    : Vornamen 2021
# Issued                   : 2023-01-25T09:24:38
# Modified                 : 2023-01-25T09:24:38
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/dc6170db-f7f4-4bdc-b790-13df55f0cf64/download/vornamen_2021.csv')

# Distribution 9
# Ktzhdistid               : 1440
# Title                    : Vornamen 2022
# Issued                   : 2023-01-26T16:37:07
# Modified                 : 2023-01-26T16:37:07
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/99ad40ec-9d7b-4a2e-87eb-9bac783fb57a/resource/5f11d3a0-4779-4f64-b113-b59326e6d839/download/open_data_portal_2022.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
