---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-23"
output: html_document
---

## Dataset: Fernzugriffsberechtigungen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/fernzugriffe)

Auto generated R starter code for data set 145@lhm.

## Metadata

- **Issued** `2022-12-13T13:24:50`
- **Modified** `2022-12-19T10:22:35`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Stadtratsauftrag']`
- **Publisher** `['it-referat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/fernzugriffe`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1451
# Title                    : Fernzugriffe
# Issued                   : 2022-12-13T13:25:36
# Modified                 : 2022-12-13T13:25:36
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/45e46e90-ff50-47bf-8f13-b334b5262c06/resource/6c9f6138-2a33-4801-9010-ea84b56721b7/download/datensatze-ready.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
