---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-21"
output: html_document
---

## Dataset: P+R Anlagen München

abcdefg

[Direct data shop link for dataset](XYZ147@lhm)

Auto generated R starter code for data set 147@lhm.

## Metadata

- **Issued** `2022-11-15T07:15:00`
- **Modified** `2022-12-12T17:12:56`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Parken', 'Stadtratsauftrag']`
- **Publisher** `['p-r-park-ride-gmbh-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/p-r-anlagen-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1471
# Title                    : Übersicht P+R Anlagen
# Description              : abcdefg
# Issued                   : 2022-11-15T07:16:18
# Modified                 : 2022-11-15T07:16:18
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a8896f06-15e0-4f29-a509-55384799fff3/resource/aff2ba04-5eb6-4dfe-bc98-4ec3ec3dfdff/download/ubersicht-pr-anlagen2.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
