---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-30"
output: html_document
---

## Dataset: P+R-Anlagen - Belegungsprognosen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/p-r-anlagen-belegungsprognosen)

Auto generated R starter code for data set 148@lhm.

## Metadata

- **Issued** `2022-11-15T07:25:49`
- **Modified** `2022-12-12T17:13:20`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Parken', 'Stadtratsauftrag']`
- **Publisher** `['p-r-park-ride-gmbh-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/p-r-anlagen-belegungsprognosen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1481
# Title                    : Belegungsprognosen P+R Anlagen München
# Issued                   : 2022-11-15T07:26:12
# Modified                 : 2022-11-15T07:26:12
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/b1775816-5c15-49df-bc96-e077ca5558fd/resource/90e7fa46-3400-4fe3-b15d-aa6c74662ec5/download/belegungsprognosen-pr-anlagen-stadt-stand-10-2022-neu.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
