---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-28"
output: html_document
---

## Dataset: Ordentliche Erträge und Aufwendungen der Produkte der LHM

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/ordentliche-ertraege-und-aufwendungen-produkte-der-lhm)

Auto generated R starter code for data set 149@lhm.

## Metadata

- **Issued** `2022-11-15T07:46:06`
- **Modified** `2022-12-12T17:06:27`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Stadtratsauftrag']`
- **Publisher** `['stadtkaemmerei']`
- **Landingpage** `https://opendata.muenchen.de/dataset/ordentliche-ertraege-und-aufwendungen-produkte-der-lhm`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1491
# Title                    : Ordentliche Erträge und Aufwendungen LHM-Produkte
# Description              : abcdefg
# Issued                   : 2022-11-15T07:47:50
# Modified                 : 2022-11-15T07:47:50
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a3c1e1f2-9fa5-4efb-ad64-b269c746e742/resource/fc16d07d-89c7-4b74-989d-41427ab089be/download/02_ska_produktuebersicht_oe_oa_bay_p_2022r_opendata.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
