---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-16"
output: html_document
---

## Dataset: Haltestellenliste MVV

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/haltestellenliste-mvv)

Auto generated R starter code for data set 153@lhm.

## Metadata

- **Issued** `2022-09-16T13:03:30`
- **Modified** `2022-12-12T17:03:11`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['MVV', 'Stadtratsauftrag']`
- **Publisher** `['muenchner-verkehrs-und-tarifverbund-gmbh-mvv']`
- **Landingpage** `https://opendata.muenchen.de/dataset/haltestellenliste-mvv`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1531
# Title                    : Haltestellenliste MVV
# Issued                   : 2022-09-16T13:05:03
# Modified                 : 2022-09-16T13:05:03
# Rights                   : cc-by

df <- read_delim('https://www.mvv-muenchen.de/fileadmin/mediapool/02-Fahrplanauskunft/03-Downloads/openData/20-01-MVV_HST-_s20-o-T.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
