---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-23"
output: html_document
---

## Dataset: Geburten in der München Klinik gGmbH

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/geburten-in-der-muenchen-klinik-ggmbh)

Auto generated R starter code for data set 156@lhm.

## Metadata

- **Issued** `2022-12-12T14:49:13`
- **Modified** `2022-12-12T17:01:45`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Krankenhaus', 'Stadtratsauftrag']`
- **Publisher** `['muenchen-klinik-ggmbh']`
- **Landingpage** `https://opendata.muenchen.de/dataset/geburten-in-der-muenchen-klinik-ggmbh`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1561
# Title                    : Geburten in der München Klinik gGmbh
# Issued                   : 2022-12-12T14:51:19
# Modified                 : 2022-12-12T14:51:19
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a872618b-d29d-43f8-ae79-cb27ca8b9f23/resource/0a8a0026-c95a-40dc-bfb6-83c2011a2439/download/open-data-munchen-klinik_geburten_bearbeitet.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
