---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-16"
output: html_document
---

## Dataset: Schulen und Schülerzahlen in München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/schulen-und-schuelerzahlen-in-muenchen)

Auto generated R starter code for data set 157@lhm.

## Metadata

- **Issued** `2022-12-12T16:10:18`
- **Modified** `2022-12-12T17:01:11`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Schule', 'Stadtratsauftrag']`
- **Publisher** `['referat-fur-bildung-und-sport']`
- **Landingpage** `https://opendata.muenchen.de/dataset/schulen-und-schuelerzahlen-in-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1571
# Title                    : Schulen und Schülerzahlen Schuljahr 2020/21
# Issued                   : 2022-12-12T16:11:46
# Modified                 : 2022-12-12T16:11:46
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4e7880e0-c91a-4f17-8e0f-9cd8e7d7215f/resource/00e6fc97-7613-4151-a067-1ecb1920f50d/download/bearbeitet-opendata_rbs_a_b_schulen_schuelerzahlen.csv')

# Distribution 1
# Ktzhdistid               : 1572
# Title                    : Schulen und Schülerzahlen Schuljahr 2021/22
# Issued                   : 2022-12-12T16:12:14
# Modified                 : 2022-12-12T16:12:14
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4e7880e0-c91a-4f17-8e0f-9cd8e7d7215f/resource/3eff771f-5dca-41d6-b4ec-7d323905ee91/download/bearbeitet-opendata_rbs_a_b_schulen_schulerzahlen-sj-2021_22.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
