---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-24"
output: html_document
---

## Dataset: Daten Tierpark Hellabrunn

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-tierpark-hellabrunn)

Auto generated R starter code for data set 158@lhm.

## Metadata

- **Issued** `2022-12-12T16:28:35`
- **Modified** `2022-12-12T17:00:53`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Stadtratsauftrag', 'Tierpark', 'Zoo']`
- **Publisher** `['muenchener-tierpark-hellabrunn-ag']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-tierpark-hellabrunn`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1581
# Title                    : Daten Tierpark Hellabrunn
# Issued                   : 2022-12-12T16:30:00
# Modified                 : 2022-12-12T16:30:00
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4fe2935a-88e8-4752-b5b4-2d282cb911f7/resource/82c679fe-97f3-4e97-8fd2-d5839f0b8856/download/datensatze-tierpark-fur-open-data-portal.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
