---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-20"
output: html_document
---

## Dataset: Belegung Gewerbehöfe

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/belegung-gewerbehoefe)

Auto generated R starter code for data set 159@lhm.

## Metadata

- **Issued** `2022-12-12T16:35:58`
- **Modified** `2022-12-12T17:00:38`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Stadtratsauftrag']`
- **Publisher** `['munchner-gewerbehof-und-technologiezentrumsgesellschaft-mbh']`
- **Landingpage** `https://opendata.muenchen.de/dataset/belegung-gewerbehoefe`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1591
# Title                    : Belegung Gewerbehöfe
# Issued                   : 2022-12-12T16:36:24
# Modified                 : 2022-12-12T16:36:24
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/6c8f0118-441d-47fc-a0c3-9dd2789b1cfd/resource/eb8f8471-9993-485c-81d9-1d3a8e6e8094/download/belegung-gh-ab-2010.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
