---
title: "Open Government Data, provided by Landeshauptstadt M체nchen"
date: "2023-09-21"
output: html_document
---

## Dataset: Mobilit채tspunkte

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/15@lhm)

Auto generated R starter code for data set 15@lhm.

## Metadata

- **Issued** `2023-09-01T01:00:09`
- **Modified** `2023-09-21T01:00:12`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Digitaler Zwilling M체nchen', 'Karte', 'Mobilit채tspunkte', 'infoMapAccessService']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/mobilitaetspunkte`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 155
# Title                    : WFS (CSV)
# Description              : abcdefg
# Issued                   : 2023-09-21T01:00:14
# Modified                 : 2023-09-21T01:00:14
# Rights                   : dl-by-de/2.0

df <- read_delim('http://geoportal.muenchen.de/geoserver/mor_wfs/ows?service=WFS&amp;version=1.1.0&amp;request=GetFeature&amp;typeName=mor_wfs:mobilitaetspunkte&amp;outputFormat=csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

MOR | Data Shop | gis.mor@muenchen.de
