---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-04"
output: html_document
---

## Dataset: Monatszahlen Gewerbe

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/monatszahlen-gewerbe)

Auto generated R starter code for data set 160@lhm.

## Metadata

- **Issued** `2017-02-20T11:04:38`
- **Modified** `2022-11-28T10:50:25`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Monatszahlen']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/monatszahlen-gewerbe`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1601
# Title                    : Monatszahlen Gewerbe
# Issued                   : 2017-02-20T12:04:54
# Modified                 : 2017-11-09T07:24:08
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/92d4a8dc-bc7f-487c-a624-903033abe355/resource/208435d3-e3a9-46a2-b2ed-69218ee6d7c3/download/monatszahlen1710gewerbe.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | stat.dir@muenchen.de
