---
title: "Open Government Data, provided by Landeshauptstadt M체nchen"
date: "2023-10-13"
output: html_document
---

## Dataset: Behindertenparkpl채tze

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/behindertenparkplaetze)

Auto generated R starter code for data set 161@lhm.

## Metadata

- **Issued** `2014-12-15T14:09:27`
- **Modified** `2022-06-27T07:44:23`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Parken', 'Parkpl채tze', 'Verkehr']`
- **Publisher** `['landeshauptstadt-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/behindertenparkplaetze`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1611
# Title                    : Behindertenparkpl채tze Juni 2022
# Issued                   : 2022-06-27T07:32:43
# Modified                 : 2022-06-27T07:39:26
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/80a2d76a-ebc9-40b5-b54c-b5c8af9df65f/resource/c1166a5a-5764-47e1-92bb-2d63dab785eb/download/220624_behindertenparkplaetze_muenchen.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | egovernment@muenchen.de
