---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-27"
output: html_document
---

## Dataset: GEWOFAG Wohnungen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/gewofag-wohnungen)

Auto generated R starter code for data set 161@lhm.

## Metadata

- **Issued** `2022-08-12T07:35:27`
- **Modified** `2022-09-08T13:16:40`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['SRA', 'Wohnen', 'Wohnungen']`
- **Publisher** `['landeshauptstadt-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/gewofag-wohnungen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1611
# Title                    : Wohnungen GEWOFAG
# Issued                   : 2022-08-12T07:44:04
# Modified                 : 2022-09-08T13:09:24
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/7796e955-81f4-4541-93d6-52f5ca1c4810/resource/cdaff819-a83c-490c-848c-7324f6dcc1ad/download/open_data_meldung_gewofag_2022_umsortiert.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

GEWOFAG | Data Shop | 
