---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-09"
output: html_document
---

## Dataset: Radverkehrsanlagen im Straßenunterhalt der Landeshauptstadt München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/radverkehrsanlagen-im-strassenunterhalt-der-landeshauptstadt-muenchen)

Auto generated R starter code for data set 162@lhm.

## Metadata

- **Issued** `2022-06-14T05:28:08`
- **Modified** `2022-06-14T05:51:00`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Fahrradweg', 'Rad', 'Radverkehr', 'Radweg']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/radverkehrsanlagen-im-strassenunterhalt-der-landeshauptstadt-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1622
# Title                    : Radwege CSV-Datei
# Issued                   : 2022-06-14T05:32:48
# Modified                 : 2022-06-14T05:45:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/7ad3bc6c-4c1a-4a63-9cb2-0d613f5b69fa/resource/14977232-94f3-4cdb-94fc-1e709698ba3f/download/radwege_t2.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Baureferat | Data Shop | 
