---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-06"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München November 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2021)

Auto generated R starter code for data set 165@lhm.

## Metadata

- **Issued** `2021-12-10T16:30:18`
- **Modified** `2022-05-09T15:29:02`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1651
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München November 2021
# Issued                   : 2021-12-10T16:31:43
# Modified                 : 2022-05-09T15:29:02
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8015869b-f288-445d-a12f-1fb1e9fd3005/resource/61fced4f-dd74-46f3-9d0d-bd48fd82e341/download/rad_2021_11_15min.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
