---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-23"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München August 2020

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/166@lhm)

Auto generated R starter code for data set 166@lhm.

## Metadata

- **Issued** `2020-09-21T05:29:51`
- **Modified** `2022-03-31T05:13:25`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-august-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1661
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München August 2020
# Description              : abcdefg
# Issued                   : 2020-09-21T07:30:38
# Modified                 : 2020-09-21T05:30:38
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/37ba15ed-b94e-43dc-8ca0-5c2f107a38d3/resource/b9fa9fcd-3267-44b9-ae4a-2b143c4304d1/download/rad20200815min.csv')

# Distribution 1
# Ktzhdistid               : 1662
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München August 2020
# Description              : abcdefg
# Issued                   : 2020-09-21T07:31:10
# Modified                 : 2020-09-21T05:31:10
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/37ba15ed-b94e-43dc-8ca0-5c2f107a38d3/resource/8110cc37-fee3-4992-ab1f-5552b6c8752f/download/rad202008tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
