---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-27"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Januar 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2021)

Auto generated R starter code for data set 167@lhm.

## Metadata

- **Issued** `2021-02-12T10:39:41`
- **Modified** `2022-03-31T05:13:54`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1671
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Januar 2021
# Issued                   : 2021-02-12T11:41:32
# Modified                 : 2021-02-12T10:41:32
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/db8c69e8-f7ac-44a6-82f6-8e8c8c8f3369/resource/73c321e3-606c-4e9d-8cfb-d76c7529f5ba/download/rad20210115min.csv')

# Distribution 1
# Ktzhdistid               : 1672
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Januar 2021
# Issued                   : 2021-02-12T11:42:47
# Modified                 : 2021-02-12T10:42:47
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/db8c69e8-f7ac-44a6-82f6-8e8c8c8f3369/resource/dff8d249-c952-40e0-8bdc-4dda1634b409/download/rad202101tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
