---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-18"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juni 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2019)

Auto generated R starter code for data set 169@lhm.

## Metadata

- **Issued** `2019-08-05T06:49:33`
- **Modified** `2022-03-31T05:13:05`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1691
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Juni 2019
# Issued                   : 2019-08-05T08:50:14
# Modified                 : 2019-08-05T06:50:14
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2778adcb-f051-4837-adec-34dc19343f30/resource/87728670-5788-415a-9ed4-0bbb5a859c51/download/rad20190615min.csv')

# Distribution 1
# Ktzhdistid               : 1692
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juni 2019
# Issued                   : 2019-08-05T08:50:32
# Modified                 : 2019-10-29T12:37:06
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2778adcb-f051-4837-adec-34dc19343f30/resource/422569b2-e753-4bfc-8e05-51b79c290cda/download/rad201906tageneu.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
