---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-04"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München September 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2021)

Auto generated R starter code for data set 172@lhm.

## Metadata

- **Issued** `2021-10-26T13:11:50`
- **Modified** `2021-11-04T12:41:58`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1721
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München September 2021
# Issued                   : 2021-10-26T13:13:08
# Modified                 : 2021-11-04T12:41:35
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/245d0a6a-2b33-4afa-95d4-4043e8d55eb2/resource/4cb7280b-003e-43fb-8fea-3eb4b165f1cf/download/rad_2021_09_15min.csv')

# Distribution 1
# Ktzhdistid               : 1722
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München September 2021
# Issued                   : 2021-10-26T13:13:54
# Modified                 : 2021-11-04T12:41:58
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/245d0a6a-2b33-4afa-95d4-4043e8d55eb2/resource/d5c8ea45-1400-4029-b957-8495d3ce1148/download/rad_2021_09_tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
