---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-25"
output: html_document
---

## Dataset: Bevölkerung Stadtbezirksteile München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/bevoelkerung-stadtbezirksteile-muenchen)

Auto generated R starter code for data set 174@lhm.

## Metadata

- **Issued** `2018-03-27T07:48:02`
- **Modified** `2021-10-27T14:59:57`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/bevoelkerung-stadtbezirksteile-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1741
# Title                    : Hauptwohnsitzbevölkerung Stadtbezirksteile
# Issued                   : 2018-03-27T09:48:22
# Modified                 : 2018-03-27T07:48:22
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/15aa8720-cd0c-45db-ba37-d90924a9dc5c/resource/ffcdc8ec-1fc4-4186-9fbf-9114448e80a7/download/bevoelkerunghws201712stadtbezirksteile.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
