---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-12"
output: html_document
---

## Dataset: M-WLAN Hotspots

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/m-wlan-hotspots)

Auto generated R starter code for data set 174@lhm.

## Metadata

- **Issued** `2015-02-20T10:32:02`
- **Modified** `2021-09-28T06:18:33`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Hotspot', 'Mobile', 'WiFi']`
- **Publisher** `['landeshauptstadt-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/m-wlan-hotspots`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1741
# Title                    : M-WLAN Hotspots
# Issued                   : 2015-02-20T11:33:40
# Modified                 : 2016-07-12T08:42:45
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2f256473-423d-4c3d-846c-09977aa31205/resource/4ac5b616-ebbf-4857-ae79-43369d6c4c87/download/m-wlan2015-01-21.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | egovernment@muenchen.de
