---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-24"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München November 2017

{{ DATASET_DESCRIPTION }}

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2017)

Auto generated R starter code for data set 175@lhm.

## Metadata

- **Issued** `2018-09-20T06:37:14`
- **Modified** `2021-09-28T06:19:48`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1751
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München November 2017
# Issued                   : 2018-09-20T08:37:47
# Modified                 : 2018-09-20T06:37:47
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/f27430b0-2f95-4b3f-8436-c984377ec3b8/resource/b71ca8a2-d881-4156-86a6-f03eaf326caf/download/rad20171115min.csv')

# Distribution 1
# Ktzhdistid               : 1752
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München November 2017
# Issued                   : 2018-09-20T08:38:16
# Modified                 : 2018-09-20T06:38:16
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/f27430b0-2f95-4b3f-8436-c984377ec3b8/resource/48e34f1e-8416-4b4d-8531-727ac2c794aa/download/rad201711tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
