---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-24"
output: html_document
---

## Dataset: Privathaushalte in den Stadtbezirken

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/176@lhm)

Auto generated R starter code for data set 176@lhm.

## Metadata

- **Issued** `2015-04-23T05:27:48`
- **Modified** `2021-09-28T06:15:26`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Haushalte', 'Stadtbezirke']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/privathaushalte-in-den-stadtbezirken`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1761
# Title                    : Privathaushalte in den Stadtbezirken zum 31.12.2013
# Description              : abcdefg
# Issued                   : 2015-04-23T07:28:31
# Modified                 : 2015-04-23T07:33:16
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/cb0e5a0b-2a87-4a29-9b70-69e1db4fb529/resource/ce4bc761-84c1-4a3e-80d8-dd51577fb18f/download/privathaushaltestadtbezirke2013.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | egovernment@muenchen.de
