---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-12-05"
output: html_document
---

## Dataset: Bevölkerung in den Stadtbezirken

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/bevoelkerung-stadtbezirken)

Auto generated R starter code for data set 177@lhm.

## Metadata

- **Issued** `2015-04-22T11:44:00`
- **Modified** `2021-09-28T06:17:58`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Stadtbezirke']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/bevoelkerung-stadtbezirken`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1771
# Title                    : Bevölkerung in den Stadtbezirken am 31.12.2013
# Issued                   : 2015-04-23T07:09:43
# Modified                 : 2015-04-23T07:17:42
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/e3f5dbd2-39cc-40cd-bc91-4bb49a0b1802/resource/a641ce6a-4e01-4f4b-9976-1ae6a47e3762/download/jt140102.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | egovernment@muenchen.de
