---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-23"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München März 2019

{{ DATASET_DESCRIPTION }}

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/daten-der-raddauerzaehlstellen-muenchen-maerz-2019)

Auto generated R starter code for data set 179@lhm.

## Metadata

- **Issued** `2019-05-08T06:50:45`
- **Modified** `2021-09-28T06:14:37`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-maerz-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1791
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München März 2019
# Issued                   : 2019-05-08T08:51:39
# Modified                 : 2019-05-08T06:51:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/72d7cf3d-8218-4895-b928-699c0a200885/resource/f77c81aa-dccc-43d4-9fb6-d53c4aa0487c/download/rad20190315min.csv')

# Distribution 1
# Ktzhdistid               : 1792
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München März 2019
# Issued                   : 2019-05-08T08:52:24
# Modified                 : 2019-05-08T06:52:24
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/72d7cf3d-8218-4895-b928-699c0a200885/resource/f1b65131-95ca-43dd-bbb0-56d300ee6331/download/rad201903tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
