---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-27"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Januar 2017

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2017)

Auto generated R starter code for data set 180@lhm.

## Metadata

- **Issued** `2018-09-19T07:17:49`
- **Modified** `2021-09-28T06:13:51`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1801
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Januar 2017
# Issued                   : 2018-09-19T09:27:48
# Modified                 : 2018-09-19T07:27:48
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/011c0015-8e1c-4c94-af9a-bd5ba118b6e9/resource/9f3b9a02-8782-4e1a-935a-1516fc78b719/download/rad20170115min.csv')

# Distribution 1
# Ktzhdistid               : 1802
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Januar 2017
# Issued                   : 2018-09-19T09:28:22
# Modified                 : 2018-09-19T07:28:22
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/011c0015-8e1c-4c94-af9a-bd5ba118b6e9/resource/c42b2895-e9df-4c1f-9562-8f3c6839108b/download/rad201701tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
