---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-02"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Dezember 2017

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-dezember-2017)

Auto generated R starter code for data set 181@lhm.

## Metadata

- **Issued** `2018-09-20T08:32:35`
- **Modified** `2021-09-28T06:08:08`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-dezember-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1811
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Dezember 2017
# Issued                   : 2018-09-20T10:33:16
# Modified                 : 2018-09-20T08:33:16
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/77f13894-918e-481b-af7c-c2b3d40105dc/resource/ba1e478b-d736-4e96-9b7d-53c090b95cb1/download/rad20171215min.csv')

# Distribution 1
# Ktzhdistid               : 1812
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Dezember 2017
# Issued                   : 2018-09-20T10:33:44
# Modified                 : 2018-10-02T06:20:03
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/77f13894-918e-481b-af7c-c2b3d40105dc/resource/9a0a1db6-8273-4b5a-9474-8aefa3a5629f/download/rad201712tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
