---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-17"
output: html_document
---

## Dataset: Bruttolastgang elektrische Energie der Stadt Winterthur

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/1863@stadt-winterthur)

Auto generated R starter code for data set 1863@stadt-winterthur.

## Metadata

- **Issued** `2022-11-25T09:02:55`
- **Modified** `2023-10-17T10:10:41`
- **Startdate** `2013-01-01`
- **Enddate** `2023-10-16`
- **Theme** `['Energie']`
- **Keyword** `['gemeinden', 'strom', 'stromverbrauch', 'ogd']`
- **Publisher** `['Stadt Winterthur']`
- **Landingpage** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 4 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 3561
# Title                    : Energieverbrauch als Bruttolastgang 2013-2015
# Description              : Der Bruttolastgang wird pro Viertelstunde in Kilowattstunden zusammengefasst.
# Issued                   : 2022-11-25T09:02:55
# Modified                 : 2022-11-25T09:02:55
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00001863_00003561.csv')

# Distribution 1
# Ktzhdistid               : 3562
# Title                    : Energieverbrauch als Bruttolastgang ab 2022
# Description              : Der Bruttolastgang wird pro Viertelstunde in Kilowattstunden zusammengefasst.
# Issued                   : 2022-11-25T09:02:55
# Modified                 : 2023-10-17T10:10:41
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00001863_00003562.csv')

# Distribution 2
# Ktzhdistid               : 3563
# Title                    : Energieverbrauch als Bruttolastgang 2016-2018
# Description              : Der Bruttolastgang wird pro Viertelstunde in Kilowattstunden zusammengefasst.
# Issued                   : 2022-11-25T09:02:55
# Modified                 : 2022-11-25T09:02:55
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00001863_00003563.csv')

# Distribution 3
# Ktzhdistid               : 3564
# Title                    : Energieverbrauch als Bruttolastgang 2019-2021
# Description              : Der Bruttolastgang wird pro Viertelstunde in Kilowattstunden zusammengefasst.
# Issued                   : 2022-11-25T09:02:55
# Modified                 : 2022-11-25T09:02:55
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceNotRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00001863_00003564.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Stadt Winterthur | Stadtwerk Winterthur | stadtwerk.messdaten@win.ch
