---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-23"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juni 2017

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2017)

Auto generated R starter code for data set 186@lhm.

## Metadata

- **Issued** `2018-09-19T12:27:08`
- **Modified** `2021-09-27T12:34:10`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1861
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Juni 2017
# Issued                   : 2018-09-19T14:28:04
# Modified                 : 2018-09-19T12:28:04
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/dda40d14-4592-4fe2-8057-21208bc57ec2/resource/c0b9f554-ea43-4d43-8654-57fbcfb079d5/download/rad20170615min.csv')

# Distribution 1
# Ktzhdistid               : 1862
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juni 2017
# Issued                   : 2018-09-19T14:28:42
# Modified                 : 2018-09-19T12:28:42
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/dda40d14-4592-4fe2-8057-21208bc57ec2/resource/0dbe1c6e-cf96-41c4-a903-ff1539af6c88/download/rad201706tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
