---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-26"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München März 2017

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-maerz-2017)

Auto generated R starter code for data set 186@lhm.

## Metadata

- **Issued** `2018-09-19T09:02:04`
- **Modified** `2021-09-27T12:22:18`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-maerz-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1861
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München März 2017
# Description              : abcdefg
# Issued                   : 2018-09-19T11:02:29
# Modified                 : 2018-09-19T09:02:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/c9af32b1-fc32-4099-be51-4df58a577919/resource/74810400-6740-4f23-842d-f1f8618dc8f7/download/rad20170315min.csv')

# Distribution 1
# Ktzhdistid               : 1862
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München März 2017
# Description              : abcdefg
# Issued                   : 2018-09-19T11:03:02
# Modified                 : 2018-09-19T09:03:02
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/c9af32b1-fc32-4099-be51-4df58a577919/resource/9036aca9-729d-44e2-aa8b-8937248bec76/download/rad201703tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
