---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-11"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Februar 2017

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-februar-2017)

Auto generated R starter code for data set 187@lhm.

## Metadata

- **Issued** `2018-09-19T08:09:43`
- **Modified** `2021-09-27T12:23:46`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2017']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-februar-2017`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1871
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Februar 2017
# Issued                   : 2018-09-19T10:10:30
# Modified                 : 2018-09-19T08:10:30
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4def19b1-7b05-4a0c-ad6d-0d1061e88038/resource/66ab7797-e225-4f20-9dfd-efa1f984fb7d/download/rad201702tage.csv')

# Distribution 1
# Ktzhdistid               : 1872
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Februar 2017
# Issued                   : 2018-09-19T10:11:00
# Modified                 : 2018-09-19T08:11:00
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4def19b1-7b05-4a0c-ad6d-0d1061e88038/resource/3c367280-32de-4598-8352-4b2d780214c6/download/rad20170215min.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
