---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-28"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München April 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2021)

Auto generated R starter code for data set 192@lhm.

## Metadata

- **Issued** `2021-05-03T13:45:39`
- **Modified** `2021-09-27T12:10:22`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1921
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München April 2021
# Issued                   : 2021-05-03T15:46:46
# Modified                 : 2021-05-03T13:46:46
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a569aa0e-5098-4701-8101-2e715b628f41/resource/4d38fbe0-1e64-4677-b16a-11b80a9a6d06/download/rad20210415min.csv')

# Distribution 1
# Ktzhdistid               : 1922
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München April 2021
# Issued                   : 2021-05-03T15:47:43
# Modified                 : 2021-05-03T13:47:43
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a569aa0e-5098-4701-8101-2e715b628f41/resource/8f9a0723-a70c-4f5a-b42a-58d88baffd32/download/rad202104tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
