---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-14"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juni 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2021)

Auto generated R starter code for data set 192@lhm.

## Metadata

- **Issued** `2021-08-27T06:30:56`
- **Modified** `2021-09-27T12:07:32`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1921
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Juni 2021
# Issued                   : 2021-08-27T06:31:55
# Modified                 : 2021-08-27T06:31:55
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/460641f5-52e7-48fd-96db-3413caba9688/resource/2872d047-afb2-443f-b999-176709d930c1/download/rad_2021_06_15min.csv')

# Distribution 1
# Ktzhdistid               : 1922
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juni 2021
# Issued                   : 2021-08-27T06:32:47
# Modified                 : 2021-08-27T06:32:47
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/460641f5-52e7-48fd-96db-3413caba9688/resource/4e432546-8be8-43a7-a602-aa3361ad7d75/download/rad_2021_06_tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
