---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-12"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juli 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juli-2018)

Auto generated R starter code for data set 194@lhm.

## Metadata

- **Issued** `2018-09-04T14:11:00`
- **Modified** `2021-09-27T11:12:07`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juli-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1941
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Juli 2018
# Issued                   : 2018-09-04T16:13:03
# Modified                 : 2018-09-04T14:13:03
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/26eeb32f-489b-43d9-ac55-c954c7c643fd/resource/fb305c18-68db-4e95-9dcd-0cf7d163b496/download/rad20180715min.csv')

# Distribution 1
# Ktzhdistid               : 1942
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juli 2018
# Issued                   : 2018-09-04T16:17:15
# Modified                 : 2018-09-04T14:18:51
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/26eeb32f-489b-43d9-ac55-c954c7c643fd/resource/7368547c-7118-49bf-9286-e510ea621c58/download/rad201807tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
