---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-21"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München September 2020

abcdefg

[Direct data shop link for dataset](XYZ198@lhm)

Auto generated R starter code for data set 198@lhm.

## Metadata

- **Issued** `2020-10-13T09:58:59`
- **Modified** `2021-09-27T07:52:30`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1981
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München September 2020
# Description              : abcdefg
# Issued                   : 2020-10-13T12:00:13
# Modified                 : 2020-10-13T10:00:13
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/13e1fa56-4b8e-47fe-a9fa-210890bab968/resource/f7fbca17-c54f-44d8-ae94-7009a1c37bee/download/rad20200915min.csv')

# Distribution 1
# Ktzhdistid               : 1982
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München September 2020
# Description              : abcdefg
# Issued                   : 2020-10-13T12:44:50
# Modified                 : 2020-10-13T10:44:50
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/13e1fa56-4b8e-47fe-a9fa-210890bab968/resource/d8149405-208b-4561-b2d2-ad0a1ed06af0/download/rad202009tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
