---
title: "Open Government Data, provided by Landeshauptstadt M체nchen"
date: "2023-11-24"
output: html_document
---

## Dataset: Stadtplan der st채dtischen Trinkbrunnen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/opendata_trinkwasserbrunnen)

Auto generated R starter code for data set 19@lhm.

## Metadata

- **Issued** `2023-08-02T13:23:50`
- **Modified** `2023-10-17T01:00:18`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Digitaler Zwilling M체nchen', 'Landeshauptstadt M체nchen', 'Service']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/opendata_trinkwasserbrunnen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 193
# Title                    : WFS (CSV)
# Issued                   : 2023-10-17T01:00:22
# Modified                 : 2023-10-17T01:00:22
# Rights                   : dl-by-de/2.0

df <- read_delim('http://geoportal.muenchen.de/geoserver/baug_wfs/ows?service=WFS&amp;version=1.0.0&amp;request=GetFeature&amp;typeName=baug_wfs:opendata_trinkwasserbrunnen&amp;outputFormat=csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

BAU-GS | Data Shop | brunnen.denkmaeler@muenchen.de
