---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-25"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juni 2020

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2020)

Auto generated R starter code for data set 202@lhm.

## Metadata

- **Issued** `2020-07-10T14:13:44`
- **Modified** `2021-09-27T06:30:20`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2021
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen MünchenJuni 2020
# Issued                   : 2020-07-10T16:14:29
# Modified                 : 2020-07-10T14:14:29
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/92a78630-2c08-4a48-8714-32630d068d44/resource/3bc66619-efcd-45be-9d45-d4074673c128/download/rad20200615min.csv')

# Distribution 1
# Ktzhdistid               : 2022
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juni 2020
# Issued                   : 2020-07-10T16:15:15
# Modified                 : 2020-07-10T14:15:15
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/92a78630-2c08-4a48-8714-32630d068d44/resource/5da10532-c118-4a8f-af59-d29d3a808d44/download/rad202006tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
