---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-11"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Mai 2020

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2020)

Auto generated R starter code for data set 203@lhm.

## Metadata

- **Issued** `2020-06-03T09:43:02`
- **Modified** `2021-09-27T06:29:07`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2031
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Mai 2020
# Issued                   : 2020-06-03T11:45:49
# Modified                 : 2020-06-03T09:45:49
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/21a0987f-e822-413d-95d2-17f9c513c305/resource/57c8b8c0-4f1f-494b-8e35-e89800eea19e/download/rad20200515min.csv')

# Distribution 1
# Ktzhdistid               : 2032
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Mai 2020
# Issued                   : 2020-06-03T11:46:51
# Modified                 : 2020-06-03T09:46:51
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/21a0987f-e822-413d-95d2-17f9c513c305/resource/1c67f607-b14d-4f1d-a0d0-003dcb60f7a1/download/rad202005tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
