---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-01"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München April 2020

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2020)

Auto generated R starter code for data set 204@lhm.

## Metadata

- **Issued** `2020-05-18T04:52:36`
- **Modified** `2021-09-27T06:27:35`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2041
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München April 2020
# Issued                   : 2020-05-18T06:53:27
# Modified                 : 2020-05-18T04:53:27
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/fafb47de-59b4-49ae-946c-a82c4da94ed8/resource/178c9660-7a44-4d89-ab7e-7a92db67f9d2/download/rad20200415min.csv')

# Distribution 1
# Ktzhdistid               : 2042
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München April 2020
# Issued                   : 2020-05-18T06:54:17
# Modified                 : 2021-01-07T06:51:15
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/fafb47de-59b4-49ae-946c-a82c4da94ed8/resource/02d3b3e8-8ef7-4a00-8186-b9038957452b/download/rad202004tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
