---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-21"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Januar 2020

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2020)

Auto generated R starter code for data set 206@lhm.

## Metadata

- **Issued** `2020-02-12T13:57:09`
- **Modified** `2021-09-27T05:56:09`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2020']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2020`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2061
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Januar 2020
# Issued                   : 2020-02-12T14:58:06
# Modified                 : 2020-02-12T13:58:06
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/c63a040e-0307-48de-9de9-19f55bd9e938/resource/bed75fcd-6a04-4907-b628-7f7408fe3f21/download/rad20200115min.csv')

# Distribution 1
# Ktzhdistid               : 2062
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Januar 2020
# Issued                   : 2020-02-12T14:58:41
# Modified                 : 2020-02-12T13:58:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/c63a040e-0307-48de-9de9-19f55bd9e938/resource/99fad795-d999-4fa8-ad99-4bed0312f355/download/rad202001tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
