---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2024-01-30"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Dezember 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-dezember-2019)

Auto generated R starter code for data set 208@lhm.

## Metadata

- **Issued** `2020-01-08T07:49:43`
- **Modified** `2021-09-17T13:11:58`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-dezember-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2081
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Dezember 2019
# Issued                   : 2020-01-08T08:50:21
# Modified                 : 2020-01-08T07:50:20
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/7840db73-d293-40d0-82c7-9a67fab70734/resource/74368767-f877-49c4-b908-102b0dddf2a5/download/rad20191215min.csv')

# Distribution 1
# Ktzhdistid               : 2082
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Dezember 2019
# Issued                   : 2020-01-08T08:50:54
# Modified                 : 2020-01-08T07:50:54
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/7840db73-d293-40d0-82c7-9a67fab70734/resource/def548e1-14ae-48c2-aba9-070ff81313bb/download/rad201912tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
