---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-03"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München November 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2019)

Auto generated R starter code for data set 209@lhm.

## Metadata

- **Issued** `2020-01-08T07:38:59`
- **Modified** `2021-09-17T13:10:36`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2091
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München November 2019
# Issued                   : 2020-01-08T08:39:50
# Modified                 : 2020-01-08T07:39:50
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4bca92b3-95dd-4822-a171-468a2bc0dfbd/resource/deec23c1-7121-4042-b2e3-67577e97c776/download/rad20191115min.csv')

# Distribution 1
# Ktzhdistid               : 2092
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München November 2019
# Issued                   : 2020-01-08T08:40:17
# Modified                 : 2020-01-08T07:40:17
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4bca92b3-95dd-4822-a171-468a2bc0dfbd/resource/d8917e9c-dc75-41e7-98c4-91b9514a46f5/download/rad201911tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
