---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-04"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München September 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2019)

Auto generated R starter code for data set 211@lhm.

## Metadata

- **Issued** `2019-10-15T09:56:00`
- **Modified** `2021-09-17T12:17:39`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2111
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München September 2019
# Issued                   : 2019-10-15T11:56:39
# Modified                 : 2019-10-15T09:56:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/35e98c7b-72e0-4791-9b7b-3fc0cde17a49/resource/25597be4-ee1c-4370-afa8-90f547f2f2e5/download/rad20190915min.csv')

# Distribution 1
# Ktzhdistid               : 2112
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München September 2019
# Issued                   : 2019-10-15T11:57:05
# Modified                 : 2019-10-15T09:57:05
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/35e98c7b-72e0-4791-9b7b-3fc0cde17a49/resource/0e928a89-2511-428b-b99b-bf23a4dc1387/download/rad201909tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
