---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-30"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München August 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-august-2019)

Auto generated R starter code for data set 212@lhm.

## Metadata

- **Issued** `2019-09-05T06:24:25`
- **Modified** `2021-09-17T12:15:53`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-august-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2121
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München August 2019
# Issued                   : 2019-09-05T08:25:09
# Modified                 : 2019-09-05T06:25:09
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/126c1d3d-3bd2-4286-9d99-c2e36930979c/resource/8c548b17-ceaa-464b-bcac-11ad7ee5a3d0/download/rad20190815min.csv')

# Distribution 1
# Ktzhdistid               : 2122
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München August 2019
# Issued                   : 2019-09-05T08:25:37
# Modified                 : 2019-09-05T06:25:37
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/126c1d3d-3bd2-4286-9d99-c2e36930979c/resource/3d567619-28dd-443d-ae16-3ff92cf96aa8/download/rad201908tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
