---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-29"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juli 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juli-2019)

Auto generated R starter code for data set 213@lhm.

## Metadata

- **Issued** `2019-08-26T07:19:12`
- **Modified** `2021-09-17T12:14:22`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juli-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2131
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Juli 2019
# Issued                   : 2019-08-26T09:20:42
# Modified                 : 2019-08-26T07:20:42
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/ca7130ef-8115-4975-ab0b-8092576b068c/resource/979f5a27-d881-4257-b863-b758e6d78595/download/rad20190715min.csv')

# Distribution 1
# Ktzhdistid               : 2132
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juli 2019
# Issued                   : 2019-08-26T09:21:28
# Modified                 : 2019-10-29T12:35:42
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/ca7130ef-8115-4975-ab0b-8092576b068c/resource/4dba28f0-bb46-45fb-9e1e-e8cf22085f2e/download/rad201907tageneu.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
