---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-24"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Mai 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2019)

Auto generated R starter code for data set 214@lhm.

## Metadata

- **Issued** `2019-06-19T06:37:40`
- **Modified** `2021-09-17T11:54:22`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2141
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Mai 2019
# Issued                   : 2019-06-19T08:38:38
# Modified                 : 2019-06-19T06:38:38
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/235da1b4-b1f4-4406-bae1-e53169e03887/resource/2cc580da-89d0-4e4c-968c-82b391338bb0/download/rad20190515min.csv')

# Distribution 1
# Ktzhdistid               : 2142
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Mai 2019
# Issued                   : 2019-06-19T08:39:09
# Modified                 : 2019-06-19T06:39:09
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/235da1b4-b1f4-4406-bae1-e53169e03887/resource/59ccd361-90ed-41a9-b251-590e16e9a763/download/rad201905tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
