---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-25"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Februar 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-februar-2019)

Auto generated R starter code for data set 216@lhm.

## Metadata

- **Issued** `2019-03-11T07:01:48`
- **Modified** `2021-09-17T09:43:41`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-februar-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2161
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Februar 2019
# Issued                   : 2019-03-11T08:02:34
# Modified                 : 2019-03-13T06:02:33
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/ef88638f-dd93-49a4-8c14-df237fe2c43d/resource/b1b09617-e613-4bcf-809d-6ac92fcd0d1b/download/rad20190215min.csv')

# Distribution 1
# Ktzhdistid               : 2162
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Februar 2019
# Issued                   : 2019-03-11T08:03:12
# Modified                 : 2019-03-13T06:06:25
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/ef88638f-dd93-49a4-8c14-df237fe2c43d/resource/e454af57-76ca-4e59-960c-ce2490b030d6/download/rad201902tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
