---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-26"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München November 2018

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/217@lhm)

Auto generated R starter code for data set 217@lhm.

## Metadata

- **Issued** `2018-12-04T07:27:15`
- **Modified** `2021-09-16T13:47:05`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-november-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2171
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München November 2018
# Description              : abcdefg
# Issued                   : 2018-12-04T08:27:54
# Modified                 : 2018-12-04T07:27:54
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/73d4d62b-eb29-445d-80d2-e46764c9569c/resource/ade699ed-fd88-4ba4-a306-8798cf91e021/download/rad20181115min.csv')

# Distribution 1
# Ktzhdistid               : 2172
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München November 2018
# Description              : abcdefg
# Issued                   : 2018-12-04T08:28:26
# Modified                 : 2018-12-04T07:28:26
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/73d4d62b-eb29-445d-80d2-e46764c9569c/resource/52a60289-1bd6-449c-bddd-b8277d9861c8/download/rad201811tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
