---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-19"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Januar 2019

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2019)

Auto generated R starter code for data set 217@lhm.

## Metadata

- **Issued** `2019-02-27T11:22:50`
- **Modified** `2021-09-17T09:41:53`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2019']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2019`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2171
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Januar 2019
# Issued                   : 2019-02-27T12:23:41
# Modified                 : 2019-02-27T11:23:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/097f12d3-dc8a-4c83-a6f4-403b8c110540/resource/3dabb519-48d9-47ff-bea5-83e3fadd7b1b/download/rad20190115min.csv')

# Distribution 1
# Ktzhdistid               : 2172
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Januar 2019
# Issued                   : 2019-02-27T12:24:17
# Modified                 : 2019-02-27T11:24:17
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/097f12d3-dc8a-4c83-a6f4-403b8c110540/resource/685dd828-a7b8-4368-b0ff-963f994e1c52/download/rad201901tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
