---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-23"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Dezember 2018

{{ DATASET_DESCRIPTION }}

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/218@lhm)

Auto generated R starter code for data set 218@lhm.

## Metadata

- **Issued** `2019-01-07T09:12:07`
- **Modified** `2021-09-16T13:48:36`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-dezember-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2181
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Dezember 2018
# Issued                   : 2019-01-07T10:13:21
# Modified                 : 2019-01-07T09:13:21
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8e74a0b6-3c28-4c86-811f-f0b036546e45/resource/35456ce5-1785-4aa1-b39c-048008440b77/download/rad20181215min.csv')

# Distribution 1
# Ktzhdistid               : 2182
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Dezember 2018
# Issued                   : 2019-01-07T10:13:53
# Modified                 : 2019-01-07T09:13:53
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8e74a0b6-3c28-4c86-811f-f0b036546e45/resource/0b256f86-66cd-434a-ac8f-d1e994a279d7/download/rad201812tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
