---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-09"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München August 2021

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-august-2021)

Auto generated R starter code for data set 218@lhm.

## Metadata

- **Issued** `2021-09-15T06:11:39`
- **Modified** `2021-09-16T13:44:51`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2021']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-august-2021`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2181
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München August 2021
# Issued                   : 2021-09-15T06:12:37
# Modified                 : 2021-09-15T06:12:36
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/700599d3-a336-47e3-8abd-64168f1b49fc/resource/ba2db7af-bfdb-489a-bf41-5f46017febd3/download/rad_2021_08_15min.csv')

# Distribution 1
# Ktzhdistid               : 2182
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München August 2021
# Issued                   : 2021-09-15T06:13:08
# Modified                 : 2021-09-15T06:13:08
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/700599d3-a336-47e3-8abd-64168f1b49fc/resource/3c09982b-bdd8-41b0-a4aa-922adf888a8a/download/rad_2021_08_tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
