---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-08"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Oktober 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-oktober-2018)

Auto generated R starter code for data set 221@lhm.

## Metadata

- **Issued** `2018-12-04T07:16:29`
- **Modified** `2021-09-16T13:43:04`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-oktober-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2211
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Oktober 2018
# Issued                   : 2018-12-04T08:22:59
# Modified                 : 2018-12-04T07:22:59
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8c45c9ed-7aac-46d6-99a8-a281cc9f90b3/resource/4feae414-7d7e-43b6-8aba-dd1774e73655/download/rad20181015min.csv')

# Distribution 1
# Ktzhdistid               : 2212
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Oktober 2018
# Issued                   : 2018-12-04T08:25:31
# Modified                 : 2018-12-04T07:25:31
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8c45c9ed-7aac-46d6-99a8-a281cc9f90b3/resource/f6104439-4f59-4c8d-896f-2b343f49c6af/download/rad201810tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
