---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-23"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München September 2018

{{ DATASET_DESCRIPTION }}

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/daten-der-raddauerzaehlstellen-muenchen-september-2018)

Auto generated R starter code for data set 222@lhm.

## Metadata

- **Issued** `2018-12-04T07:04:36`
- **Modified** `2021-09-16T13:41:35`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-september-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2221
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München September 2018
# Issued                   : 2018-12-04T08:05:28
# Modified                 : 2018-12-11T07:25:10
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4352cd03-5993-40d4-9e99-e065d364f12f/resource/2d334e8c-82b6-493f-bf57-0bbc744aa545/download/rad20180915min.csv')

# Distribution 1
# Ktzhdistid               : 2222
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München September 2018
# Issued                   : 2018-12-04T08:06:00
# Modified                 : 2019-01-04T07:01:36
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4352cd03-5993-40d4-9e99-e065d364f12f/resource/fc504fb5-9bfd-4153-9ec9-41421f5e1d7c/download/rad201809tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
