---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-11"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Mai 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2018)

Auto generated R starter code for data set 223@lhm.

## Metadata

- **Issued** `2018-09-10T09:33:08`
- **Modified** `2021-09-15T07:15:20`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-mai-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2231
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Mai 2018
# Issued                   : 2018-09-10T11:33:45
# Modified                 : 2018-09-10T09:33:45
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/83ce2a0d-7a22-409d-b2a1-2692426b747d/resource/8dd210a2-cd4d-406e-b3be-3af861a9c404/download/rad20180515min.csv')

# Distribution 1
# Ktzhdistid               : 2232
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Mai  2018
# Issued                   : 2018-09-10T11:34:24
# Modified                 : 2018-09-10T09:34:24
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/83ce2a0d-7a22-409d-b2a1-2692426b747d/resource/b4e6ddd3-715c-4e39-addf-e79e8a1cb02d/download/rad201805tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
