---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-17"
output: html_document
---

## Dataset: Raddauerzählstellen München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/raddauerzaehlstellen-muenchen)

Auto generated R starter code for data set 223@lhm.

## Metadata

- **Issued** `2018-09-03T09:46:07`
- **Modified** `2021-09-16T13:35:33`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/raddauerzaehlstellen-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2231
# Title                    : Raddauerzählstellen in München
# Issued                   : 2018-09-03T11:46:39
# Modified                 : 2021-09-16T13:33:08
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/aca4bcb6-d0ff-4634-b5b9-8b5d133ab08e/resource/211e882d-fadd-468a-bf8a-0014ae65a393/download/radzaehlstellen.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
