---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-20"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Juni 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2018)

Auto generated R starter code for data set 224@lhm.

## Metadata

- **Issued** `2018-09-05T08:55:53`
- **Modified** `2021-09-15T07:16:45`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-juni-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2241
# Title                    :  15 Minuten-Werte - Daten der Raddauerzählstellen München Juni 2018 
# Issued                   : 2018-09-05T10:56:21
# Modified                 : 2018-09-05T08:56:21
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/6467f3c5-d473-4a52-99ee-188dea48ed2d/resource/9d4d7922-f232-4a46-bb26-e23dec7520a1/download/rad20180615min.csv')

# Distribution 1
# Ktzhdistid               : 2242
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Juni 2018
# Issued                   : 2018-09-05T10:58:39
# Modified                 : 2018-09-05T08:58:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/6467f3c5-d473-4a52-99ee-188dea48ed2d/resource/6a2b9e10-b937-48bf-b09a-631a51f8cdd4/download/rad201806tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
