---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-07"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München April 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2018)

Auto generated R starter code for data set 226@lhm.

## Metadata

- **Issued** `2018-09-10T09:40:57`
- **Modified** `2021-09-15T07:14:07`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-april-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2261
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München April 2018
# Issued                   : 2018-09-10T11:41:44
# Modified                 : 2018-09-10T09:41:44
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4f982f60-73e1-4b9f-95cd-cdf83635c3c7/resource/725b8a9b-78c8-4f93-b5a9-3f1a0bd766d8/download/rad20180415min.csv')

# Distribution 1
# Ktzhdistid               : 2262
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München April 2018
# Issued                   : 2018-09-10T11:42:19
# Modified                 : 2018-09-10T09:42:19
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4f982f60-73e1-4b9f-95cd-cdf83635c3c7/resource/68e6a9e0-2b8c-4e03-9e19-c0b6e09405ae/download/rad201804tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
