---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-26"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München März 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-maerz-2018)

Auto generated R starter code for data set 227@lhm.

## Metadata

- **Issued** `2018-09-10T10:28:57`
- **Modified** `2021-09-15T07:12:23`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-maerz-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2271
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München März  2018
# Issued                   : 2018-09-10T12:31:00
# Modified                 : 2021-08-27T09:10:34
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/e47d63ec-ba1c-409b-bf76-fea0775373cd/resource/43be98e1-e73f-41e3-9327-cf6f7519b90b/download/rad_2018_03_15min.csv')

# Distribution 1
# Ktzhdistid               : 2272
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München März  2018
# Issued                   : 2018-09-10T12:31:31
# Modified                 : 2021-08-27T09:10:57
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/e47d63ec-ba1c-409b-bf76-fea0775373cd/resource/f1694c61-41e0-47aa-94c0-57992929a6c1/download/rad_2018_03_tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
