---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-05"
output: html_document
---

## Dataset: Daten der Raddauerzählstellen München Januar 2018

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2018)

Auto generated R starter code for data set 228@lhm.

## Metadata

- **Issued** `2018-09-10T10:41:41`
- **Modified** `2021-09-15T07:10:54`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Fahrrad', 'Raddauerzählstellen', 'Raddauerzählstellen 2018']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/daten-der-raddauerzaehlstellen-muenchen-januar-2018`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2281
# Title                    : 15 Minuten-Werte - Daten der Raddauerzählstellen München Januar 2018
# Issued                   : 2018-09-10T12:42:15
# Modified                 : 2018-09-10T10:42:15
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/261318dd-afd7-4bcf-b7fd-c6c9b4aebbe2/resource/767008cc-34da-42b0-b813-e900e2be9d68/download/rad20180115min.csv')

# Distribution 1
# Ktzhdistid               : 2282
# Title                    : Tageswerte und Wetter - Daten der Raddauerzählstellen München Januar  2018
# Issued                   : 2018-09-10T12:42:41
# Modified                 : 2018-09-10T10:42:41
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/261318dd-afd7-4bcf-b7fd-c6c9b4aebbe2/resource/1e26f02e-4e77-48a9-bc40-015b86d190cb/download/rad201801tage.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Mobilitätsreferat - Verkehrs- und Verhaltensdaten | Data Shop | 
