---
title: "Open Government Data, provided by Landeshauptstadt M端nchen"
date: "2023-10-15"
output: html_document
---

## Dataset: B端rgerterminals in M端nchen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/buergerterminals-muenchen)

Auto generated R starter code for data set 228@lhm.

## Metadata

- **Issued** `2020-12-16T08:50:30`
- **Modified** `2020-12-16T15:36:50`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Online-Services', 'Onlinedienste', 'eID', 'nPA']`
- **Publisher** `['it-referat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/buergerterminals-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2281
# Title                    : B端rgerterminals
# Issued                   : 2020-12-16T09:51:11
# Modified                 : 2020-12-16T08:59:12
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/4d068be7-6f96-4bd8-adda-9e57da03968c/resource/39f8a4c9-31ad-45b9-b03d-cf96798ef09c/download/burgerterminalsv6.0.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

eoGov Projekt | Data Shop | 
