---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-21"
output: html_document
---

## Dataset: Ergebnishaushalt der Landeshauptstadt M체nchen 2015

abcdefg

[Direct data shop link for dataset](XYZ230@lhm)

Auto generated R starter code for data set 230@lhm.

## Metadata

- **Issued** `2015-05-26T06:07:08`
- **Modified** `2018-04-25T10:28:37`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Haushalt']`
- **Publisher** `['stadtkaemmerei']`
- **Landingpage** `https://opendata.muenchen.de/dataset/ergebnishaushalt-der-landeshauptstadt-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2301
# Title                    : Ertr채ge und Aufwendungen 2015
# Description              : abcdefg
# Issued                   : 2015-05-26T08:07:49
# Modified                 : 2015-09-29T08:57:28
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/19c72eb4-e366-4500-8c82-55317528ab2a/resource/ebf70422-9f3e-40ca-bf52-c4cbe4c4225c/download/150929baumertragaufwandbearb.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Stadtk채mmerei Landeshauptstadt M체nchen | Data Shop | egovernment@muenchen.de
