---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-18"
output: html_document
---

## Dataset: Bundestagswahlen 2013

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/bundestagswahlen-2013)

Auto generated R starter code for data set 233@lhm.

## Metadata

- **Issued** `2014-12-17T08:35:22`
- **Modified** `2017-08-23T07:14:49`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `[]`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/bundestagswahlen-2013`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2331
# Title                    : Bundestagswahl 2013 Erststimmen nach Wahlbezirken (STAT. Amt)
# Issued                   : 2014-12-18T07:57:31
# Modified                 : 2014-12-18T07:57:31
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8dc20a65-a7d3-4786-82fa-4a8b1faba836/resource/0d8ce841-841f-45da-be03-ff7711765031/download/bundestagswahl2013erststimmenwahlbezirke.csv')

# Distribution 1
# Ktzhdistid               : 2332
# Title                    : Bundestagswahl 2013 Zweitstimmen nach Wahlbezirken
# Issued                   : 2014-12-18T15:10:00
# Modified                 : 2014-12-18T15:10:00
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/8dc20a65-a7d3-4786-82fa-4a8b1faba836/resource/7ad81fcb-4123-43bc-92a7-9e7d4c713196/download/bundestagswahl2013zweitstimmenwahlbezirke.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | egovernment@muenchen.de
