---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-28"
output: html_document
---

## Dataset: Toilettenkabinen an der Isar

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/toilettenkabinen-an-der-isar)

Auto generated R starter code for data set 234@lhm.

## Metadata

- **Issued** `2016-07-14T07:52:55`
- **Modified** `2017-02-16T12:53:06`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Isar', 'Toiletten']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/toilettenkabinen-an-der-isar`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2341
# Title                    : Toilettenkabinen an der Isar
# Issued                   : 2016-07-14T09:53:30
# Modified                 : 2016-07-18T06:56:55
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/93023da9-b960-4cff-bf18-35e0f8bd40ef/resource/1d21c4ca-6f08-4272-9307-14e3174aa18d/download/toilettenkabinen-an-der-isar-2016-07-15.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | j-spartenanfrage.bau@muenchen.de
