---
title: "Open Government Data, provided by Landeshauptstadt M端nchen"
date: "2023-12-12"
output: html_document
---

## Dataset: Points of Interest an der s端dlichen Isar

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/points-of-interest-an-der-sudlichen-isar)

Auto generated R starter code for data set 235@lhm.

## Metadata

- **Issued** `2016-06-30T12:31:09`
- **Modified** `2017-02-16T12:53:06`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Br端cken', 'Isar']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/points-of-interest-an-der-sudlichen-isar`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2351
# Title                    : POIs an der Isar
# Issued                   : 2016-06-30T14:31:59
# Modified                 : 2016-08-17T08:21:43
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/fc28edb7-0e69-47b2-814e-3fa18c68f94f/resource/6fb56066-11b2-498d-ba22-cbcc85b660b4/download/pois-an-der-isar-2016-08-09.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

eoGovernment Projekt Landeshauptstadt M端nchen | Data Shop | j-spartenanfrage.bau@muenchen.de
