---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-14"
output: html_document
---

## Dataset: Müllsammelbehälter an der Isar

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/muellsammelbehaelter-an-der-isar)

Auto generated R starter code for data set 235@lhm.

## Metadata

- **Issued** `2016-06-14T12:44:13`
- **Modified** `2017-02-16T12:53:00`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Abfall', 'Isar', 'Müll']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/muellsammelbehaelter-an-der-isar`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 2351
# Title                    : Müllsammelbehälter an der Isar
# Issued                   : 2016-06-14T14:45:28
# Modified                 : 2016-07-18T06:51:21
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/0eb348c1-72ad-4384-b573-03b7c6a826c3/resource/5ad81dfc-e30d-41c0-9189-342a43893fc5/download/muellsammelbehaelter-an-der-isar-2016-07-15.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

eoGovernment Projekt Landeshauptstadt München | Data Shop | j-spartenanfrage.bau@muenchen.de
