---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-01"
output: html_document
---

## Dataset: Elektrokleinstfahrzeuge

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/opendata_ruhver_elektokleinf_poly)

Auto generated R starter code for data set 27@lhm.

## Metadata

- **Issued** `2023-02-27T15:30:38`
- **Modified** `2023-10-17T01:00:17`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Digitaler Zwilling München', 'Landeshauptstadt München', 'Verkehrswesen']`
- **Publisher** `['mobilitaetsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/opendata_ruhver_elektokleinf_poly`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 271
# Title                    : WFS (CSV)
# Issued                   : 2023-10-17T01:00:22
# Modified                 : 2023-10-17T01:00:22
# Rights                   : dl-by-de/2.0

df <- read_delim('http://geoportal.muenchen.de/geoserver/mor_wfs/ows?service=WFS&amp;version=1.0.0&amp;request=GetFeature&amp;typeName=mor_wfs:opendata_ruhver_elektokleinf_poly&amp;outputFormat=csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

MOR-GB2.212 | Data Shop | gis.mor@muenchen.de
