---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-24"
output: html_document
---

## Dataset: Straßennetzgraf Baureferat Tiefbau

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/28@lhm)

Auto generated R starter code for data set 28@lhm.

## Metadata

- **Issued** `2023-08-10T09:14:12`
- **Modified** `2023-09-21T01:00:11`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Digitaler Zwilling München', 'Landeshauptstadt München', 'Verkehrswesen']`
- **Publisher** `['baureferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/baut_strassenabschnitte_wu`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 283
# Title                    : WFS (CSV)
# Description              : abcdefg
# Issued                   : 2023-09-21T01:00:13
# Modified                 : 2023-09-21T01:00:13
# Rights                   : dl-by-de/2.0

df <- read_delim('http://geoportal.muenchen.de/geoserver/baut_wfs/ows?service=WFS&amp;version=1.1.0&amp;request=GetFeature&amp;typeName=baut_wfs:baut_strassenabschnitte_wu&amp;outputFormat=csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

BAU-TZ2 | Data Shop | geodaten.tz2.bau@muenchen.de
