---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-19"
output: html_document
---

## Dataset: Öffentliche Toiletten der Landeshauptstadt München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/offentliche-toiletten-der-landeshauptstadt-muenchen)

Auto generated R starter code for data set 36@lhm.

## Metadata

- **Issued** `2016-03-04T12:54:10`
- **Modified** `2023-10-16T06:47:35`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `[]`
- **Publisher** `['landeshauptstadt-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/offentliche-toiletten-der-landeshauptstadt-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 361
# Title                    : Öffentliche Toiletten der Landeshauptstadt München
# Issued                   : 2016-03-04T13:54:54
# Modified                 : 2016-07-12T15:52:07
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/6d8552a7-328c-48a2-ab37-5f9caa2bfbdb/resource/cc327030-a5e4-4a27-8a99-aaa8a5ab6200/download/oeffentlichetoilettenmuenchen2016-06-28.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | eogovernment@muenchen.de
