---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-09-26"
output: html_document
---

## Dataset: Parkhäuser München

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/parkhaeuser-munchen)

Auto generated R starter code for data set 36@lhm.

## Metadata

- **Issued** `2016-11-08T09:59:44`
- **Modified** `2023-09-07T12:44:13`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Auto', 'Parken', 'Parkhaus']`
- **Publisher** `['muenchen-de']`
- **Landingpage** `https://opendata.muenchen.de/dataset/parkhaeuser-munchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 361
# Title                    : Parkhäuser München CSV
# Description              : abcdefg
# Issued                   : 2016-11-08T11:00:54
# Modified                 : 2023-09-07T12:42:06
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/addaa7d4-40be-4621-846e-c5358cbe3f26/resource/e0e0e4e1-1b25-4c04-a0ea-cf9cc8335c57/download/230907places.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
