---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-21"
output: html_document
---

## Dataset: Die Bevölkerung seit 1900

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/bevoelkerung)

Auto generated R starter code for data set 38@lhm.

## Metadata

- **Issued** `2015-02-20T10:37:46`
- **Modified** `2023-09-11T13:48:33`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/bevoelkerung`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 381
# Title                    : Die Bevölkerung seit 1900 
# Issued                   : 2015-02-20T11:39:02
# Modified                 : 2023-09-11T13:40:02
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/40ed9397-06ec-4271-8fe6-54b67fbe45fb/resource/6c7165dc-0958-4213-a004-2515be292887/download/jt1401012018.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | egovernment@muenchen.de
