---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-17"
output: html_document
---

## Dataset: Abstimmungsparolen von kantonalz端rcher und nationalen Parteien

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/444@statistisches-amt-kanton-zuerich)

Auto generated R starter code for data set 444@statistisches-amt-kanton-zuerich.

## Metadata

- **Issued** `2019-07-02T00:00:00`
- **Modified** `2023-07-11T08:28:14`
- **Startdate** `1998-11-29`
- **Enddate** `None`
- **Theme** `['Politik']`
- **Keyword** `['abstimmungen', 'eidgenoessische_volksabstimmungen', 'kantonale_volksabstimmungen', 'kantonsrat', 'politik', 'regierungsrat', 'demokratie', 'ogd']`
- **Publisher** `['Statistisches Amt des Kantons Z端rich']`
- **Landingpage** `None`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 749
# Title                    : Abstimmungsparolen von kantonalz端rcher und nationalen Parteien
# Description              : None
# Issued                   : 2019-07-02T16:21:22
# Modified                 : 2023-05-17T07:53:51
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_abstimmungsparolen.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt des Kantons Z端rich | Wahlen & Abstimmungen | wahlen@statistik.ji.zh.ch
