---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-21"
output: html_document
---

## Dataset: Indikatorenatlas: Gesundheit - Zahnärzt*Zahnärztin-Dichte

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-gesundheit-zahnaerztedichte-83r65mct)

Auto generated R starter code for data set 47@lhm.

## Metadata

- **Issued** `2015-01-26T13:03:03`
- **Modified** `2023-08-29T06:40:12`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Gesundheit', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-gesundheit-zahnaerztedichte-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 471
# Title                    : Zahnärzt*Zahnärztin-Dichte
# Issued                   : 2015-01-26T14:03:04
# Modified                 : 2023-08-29T06:40:12
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a9a165ce-61e7-4af5-93cf-11b999845f1f/resource/c3e8a012-c888-475a-8250-c650e318cbb9/download/indikat_gesundheit_zahnarzt_zahnaerztin-dichte_280823.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
