---
title: "Open Government Data, provided by Landeshauptstadt M端nchen"
date: "2023-10-11"
output: html_document
---

## Dataset: Wertstoffinseln in M端nchen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/awm_container_opendata)

Auto generated R starter code for data set 4@lhm.

## Metadata

- **Issued** `2023-02-27T15:30:38`
- **Modified** `2023-09-26T01:00:24`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Digitaler Zwilling M端nchen', 'Ver- und Entsorgung', 'opendata']`
- **Publisher** `['geodatenservice-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/awm_container_opendata`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 44
# Title                    : WFS (CSV)
# Issued                   : 2023-09-26T01:00:27
# Modified                 : 2023-09-26T01:00:27
# Rights                   : dl-by-de/2.0

df <- read_delim('http://geoportal.muenchen.de/geoserver/gsm_wfs/ows?service=WFS&amp;version=1.1.0&amp;request=GetFeature&amp;typeName=gsm_wfs:awm_container_opendata&amp;outputFormat=csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

GeodatenService M端nchen | Data Shop | geoportal@muenchen.de
