---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-11-08"
output: html_document
---

## Dataset: Indikatorenatlas: Arbeitsmarkt - (Regel-)Leistungsberechtigte - erwerbsfähig - Anteil

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-2014-arbeitsmarkt-regel-leistungsberechtigte-erwerbsfaehig-anteil-83r65mct)

Auto generated R starter code for data set 54@lhm.

## Metadata

- **Issued** `2015-01-26T13:04:30`
- **Modified** `2023-08-29T05:28:58`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Arbeitsmarkt', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-2014-arbeitsmarkt-regel-leistungsberechtigte-erwerbsfaehig-anteil-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 541
# Title                    : (Regel-)Leistungsberechtigte - erwerbsfähig - Anteil 
# Issued                   : 2015-01-26T14:04:31
# Modified                 : 2023-08-29T05:28:58
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/3f96b979-7e2a-419d-98bd-b048f40c9606/resource/99ebf331-46af-4a72-83aa-e9bab6de02bc/download/indikat_arbeitsmarkt_regel-leistungsberechtigte_-_erwerbsfaehig_-_anteil_280823.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
