---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-22"
output: html_document
---

## Dataset: Indikatorenatlas: Arbeitsmarkt - Arbeitslosen - Anteil

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-2014-arbeitsmarkt-arbeitslosendichte-83r65mct)

Auto generated R starter code for data set 57@lhm.

## Metadata

- **Issued** `2015-01-26T13:04:11`
- **Modified** `2023-08-29T05:14:18`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Arbeitslosigkeit', 'Arbeitsmarkt', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-2014-arbeitsmarkt-arbeitslosendichte-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 571
# Title                    : Arbeitslose - Anteil
# Issued                   : 2015-01-26T14:04:11
# Modified                 : 2023-08-29T05:14:18
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/0771b22f-b1e7-4480-8fe5-d641c2586f3e/resource/55a1adb0-6c06-403b-ab7f-7e6c41d18e32/download/indikat_arbeitsmarkt_arbeitslose_-_anteil_280823.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
