---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-24"
output: html_document
---

## Dataset: Landtagswahl 2023 - Wahlräume in München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/landtagswahl-2023-wahlraeume-in-muenchen)

Auto generated R starter code for data set 59@lhm.

## Metadata

- **Issued** `2023-08-08T13:29:56`
- **Modified** `2023-08-08T13:50:18`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Landtagswahl 2023', 'Wahlen']`
- **Publisher** `['kreisverwaltungsreferat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/landtagswahl-2023-wahlraeume-in-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 591
# Title                    : Wahlräume Landtagswahl 2023
# Issued                   : 2023-08-08T13:31:54
# Modified                 : 2023-08-08T13:36:35
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a888e6cf-74a3-461b-a128-7b78b8cead59/resource/b15b26c0-0667-46fc-85b9-e3c1c97d09c2/download/wahlraeume_ltw_wgs84.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Kreisverwaltungsreferat, Wahlen und Abstimmungen | Data Shop | 
