---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-14"
output: html_document
---

## Dataset: WLAN-Standorte LH München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/wlan-standorte-lhm-muenchen)

Auto generated R starter code for data set 60@lhm.

## Metadata

- **Issued** `2020-10-06T05:51:51`
- **Modified** `2023-07-31T14:06:59`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['WLAN']`
- **Publisher** `['it-referat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/wlan-standorte-lhm-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 2 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 601
# Title                    : WLAN Standorte LHM Gebäude
# Issued                   : 2020-10-06T07:53:20
# Modified                 : 2022-08-04T09:53:20
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/bec8b9e3-0e55-438b-91bd-5f6a781f3efc/resource/58691a67-9ba6-40f0-b25e-9d969af66895/download/opendata_oeffwlan_2022-08-03.csv')

# Distribution 1
# Ktzhdistid               : 602
# Title                    : WLAN Öffentliche Plätze München
# Issued                   : 2021-03-05T08:49:15
# Modified                 : 2023-07-31T14:06:59
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/bec8b9e3-0e55-438b-91bd-5f6a781f3efc/resource/df31fe96-0d7d-4d00-b93d-caf9e0e4686b/download/lhm_standorte_07_2023_29_06_23.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

data.opengov@muenchen.de | Data Shop | 
