---
title: "Open Government Data, provided by Landeshauptstadt M端nchen"
date: "2023-10-09"
output: html_document
---

## Dataset: Indikatorenatlas: Grundsch端ler*innen - Grundsch端ler*innen

abcdefg

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-grundschueler-innen-grundschueler-innen)

Auto generated R starter code for data set 61@lhm.

## Metadata

- **Issued** `2023-07-28T08:34:08`
- **Modified** `2023-07-28T11:40:57`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Indikatorenatlas', 'Schule']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-grundschueler-innen-grundschueler-innen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 611
# Title                    : Grundsch端ler*innen
# Description              : abcdefg
# Issued                   : 2023-07-28T08:34:30
# Modified                 : 2023-07-28T08:34:30
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2a89ad4b-dfe9-499e-b106-29bc5ac0cad9/resource/ca81526f-c7f5-493c-8f72-65dd422d84bf/download/indikat_grundschueler_innen_grundschueler_innen_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
