---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-29"
output: html_document
---

## Dataset: Besucher und Veranstaltungen Gasteig HP8 München

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/besucher-und-veranstaltungen-gasteig-hp8-muenchen)

Auto generated R starter code for data set 61@lhm.

## Metadata

- **Issued** `2023-04-05T09:59:11`
- **Modified** `2023-08-02T14:43:10`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Besucherzahlen', 'Gasteig', 'HP8', 'Kultur', 'Stadtratsauftrag', 'Veranstaltungen']`
- **Publisher** `['landeshauptstadt-muenchen']`
- **Landingpage** `https://opendata.muenchen.de/dataset/besucher-und-veranstaltungen-gasteig-hp8-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 611
# Title                    : Besucher und Veranstaltungszahlen Gasteig  HP8 München
# Issued                   : 2023-04-05T10:00:33
# Modified                 : 2023-04-05T10:00:33
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/745f95eb-0a97-4741-bffc-c8d23a190299/resource/cd89279a-7a70-4786-bcb1-3fc7b14f6752/download/datensaetze-gasteig.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

 | Data Shop | 
