---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-23"
output: html_document
---

## Dataset: Liste aller verfügbaren Onlinedienste der Landeshauptstadt München

{{ DATASET_DESCRIPTION }}

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/liste-aller-verfuegbaren-onlinedienste-der-landeshauptstadt-muenchen)

Auto generated R starter code for data set 64@lhm.

## Metadata

- **Issued** `2023-01-27T10:43:14`
- **Modified** `2023-07-28T09:42:32`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['E-Government']`
- **Publisher** `['it-referat']`
- **Landingpage** `https://opendata.muenchen.de/dataset/liste-aller-verfuegbaren-onlinedienste-der-landeshauptstadt-muenchen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 641
# Title                    : Liste aller verfügbaren Onlinedienste 
# Issued                   : 2023-01-27T10:44:55
# Modified                 : 2023-07-28T09:41:39
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/d818c8c6-6612-480e-9ca9-68dd56995805/resource/9292d1f9-4ac2-422d-ad6f-ad92070a66e0/download/onlineleistungen-lhm.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

E- und Open-Government-Projekt | Data Shop | 
