---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-31"
output: html_document
---

## Dataset: Indikatorenatlas: Baufertigstellungen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-baufertigstellungen)

Auto generated R starter code for data set 65@lhm.

## Metadata

- **Issued** `2019-01-30T07:06:52`
- **Modified** `2023-07-28T09:07:55`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bauen', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-baufertigstellungen`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 651
# Title                    : Baufertigstellungen
# Issued                   : 2019-01-30T08:07:42
# Modified                 : 2023-07-28T09:07:55
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/30c110e6-e16b-484f-ad94-2a8bea11db32/resource/47ea6e55-974e-483d-bf44-3f0593bd7ef7/download/indikat_bauen_baufertigstellungen_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
