---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-14"
output: html_document
---

## Dataset: Indikatorenatlas: Verkehr - Erstzulassungsanteil Personenkraftwagen

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-verkehr-erstzulassungsanteil-personenkraftwagen-83r65mct)

Auto generated R starter code for data set 67@lhm.

## Metadata

- **Issued** `2015-01-26T13:03:07`
- **Modified** `2023-07-28T08:51:07`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Indikatorenatlas', 'PKW', 'Verkehr']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-verkehr-erstzulassungsanteil-personenkraftwagen-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 671
# Title                    : Erstzulassungsanteil Personenkraftwagen
# Issued                   : 2015-01-26T14:03:08
# Modified                 : 2023-07-28T08:51:07
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/a0355288-1460-4969-bf5a-40f5a7b33051/resource/4e6bbebd-c5b9-43ee-ac6b-272f1f448105/download/indikat_verkehr_erstzulassungsanteil_personenkraftwagen_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
