---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-10-23"
output: html_document
---

## Dataset: Indikatorenatlas: Grundschüler*innen - Familiensprache - nichtdeutsch

{{ DATASET_DESCRIPTION }}

{{ LANDING }}

Auto generated R starter code for data set 70@lhm.

## Metadata

- **Issued** `2015-01-26T13:02:07`
- **Modified** `2023-07-28T08:36:18`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Indikatorenatlas', 'Schule']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-grundschueler-innen-familiensprache-nichtdeutsch-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 701
# Title                    : Familiensprache - nichtdeutsch
# Issued                   : 2015-01-26T14:02:07
# Modified                 : 2023-07-28T07:10:36
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/48cb5c83-02c6-4892-aa7f-cf689f0a5ce3/resource/e44d25b5-028b-4b75-9300-f290a0272258/download/indikat_grundschueler_innen_familiensprache_nichtdeutsch_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
