---
title: "Open Government Data, provided by Landeshauptstadt M체nchen"
date: "2023-11-17"
output: html_document
---

## Dataset: Indikatorenatlas: Fl채chen - Fl채chennutzung

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-flaechen-flaechennutzung)

Auto generated R starter code for data set 72@lhm.

## Metadata

- **Issued** `2023-07-28T06:46:10`
- **Modified** `2023-07-28T06:48:07`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-flaechen-flaechennutzung`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 721
# Title                    : Fl채chennutzung
# Issued                   : 2023-07-28T06:46:36
# Modified                 : 2023-07-28T06:46:36
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/2cb8b66f-cc3c-41fa-b15a-5ace4bd997a2/resource/fe73098e-7d65-4b25-9b76-b9c8e99e332d/download/indikat_flaechen_flaechennutzung_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
