---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-12-12"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Religionszugehörigkeit

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-religionszugehoerigkeit)

Auto generated R starter code for data set 79@lhm.

## Metadata

- **Issued** `2016-11-17T07:42:22`
- **Modified** `2023-07-28T06:24:12`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-religionszugehoerigkeit`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 791
# Title                    : Religionszugehörigkeit
# Issued                   : 2016-11-17T08:43:52
# Modified                 : 2023-07-28T06:24:12
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/55d39494-79c4-47af-b5cf-163f0712e5f9/resource/42dd45fc-2300-4b7c-bb67-05da5386e174/download/indikat_bevoelkerung_religionszugehoerigkeit_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
