---
title: "Open Government Data, provided by Landeshauptstadt München"
date: "2023-10-25"
output: html_document
---

## Dataset: Indikatorenatlas: Bevölkerung - Hochbetagte

[Direct data shop link for dataset](https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-hochbetagte-83r65mct)

Auto generated R starter code for data set 89@lhm.

## Metadata

- **Issued** `2015-01-26T13:05:17`
- **Modified** `2023-07-28T05:32:30`
- **Startdate** `None`
- **Enddate** `None`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/TECH']`
- **Keyword** `['Bevölkerung', 'Indikatorenatlas']`
- **Publisher** `['statistisches-amt']`
- **Landingpage** `https://opendata.muenchen.de/dataset/indikatorenatlas-bevoelkerung-hochbetagte-83r65mct`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 891
# Title                    : Hochbetagte
# Issued                   : 2015-01-26T14:05:17
# Modified                 : 2023-07-28T05:32:30
# Rights                   : dl-by-de/2.0

df <- read_delim('https://opendata.muenchen.de/dataset/d5de79e0-f237-4858-a19a-cfa1f4ff22a6/resource/2d8a97e3-e1b9-444c-a3a2-59e6f5b22466/download/indikat_bevoelkerung_hochbetagte_240723.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt | Data Shop | 
